### 2017-12-08 Data_csv/Paper/paper.tex
Paper.tex

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%2345678901234567890123456789012345678901234567890123456789012345678901234567890
%    1     2     3     4     5     6     7     8

%\documentclass[letterpaper, 10 pt, conference]{ieeeconf} % Comment this line out if you need a4paper

\documentclass[a4paper, 10pt, conference]{ieeeconf}   % Use this line for a4 paper

\IEEEoverridecommandlockouts               % This command is only needed if 
                             % you want to use the \thanks command

\overrideIEEEmargins                   % Needed to meet printer requirements.

% See the \addtolength command later in the file to balance the column lengths
% on the last page of the document

% The following packages can be found on http:\\www.ctan.org
%\usepackage{graphics} % for pdf, bitmapped graphics files
%\usepackage{epsfig} % for postscript graphics files
%\usepackage{mathptmx} % assumes new font selection scheme installed
%\usepackage{times} % assumes new font selection scheme installed
%\usepackage{amsmath} % assumes amsmath package installed
%\usepackage{amssymb} % assumes amsmath package installed
\usepackage{graphicx, wrapfig, framed, lipsum}
\usepackage[font={small,it}]{caption}
\usepackage{subcaption}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{enumitem}
\usepackage{gensymb}
\usepackage{float}
\usepackage{hyperref}
\pagenumbering{roman}
\usepackage{pdflscape}
\usepackage{rotating}

\usepackage{xltxtra}
\setmainfont{Cambria}

\usepackage{filecontents}
\begin{filecontents*}{\jobname.bib}

@ARTICLE{Bioremediation, 
	author = { Bing Zhao, Chit Laa Poh}, 
	title  = {“Insights into environmental bioremediation by microorganisms through functional genomics and proteomics”}, 
	year  = {2008}, 
	journal = {Proteomics}, 
	volume = {8}, 
	number = {1}, 
	pages  = {874–881}
}
@ARTICLE{pseudomonas_putida, 
	author = {Rüegg and al., I.}, 
	title  = {Dynamics of Benzene and Toluene Degradation in Pseudomonas putida F1 in the Presence of the Alternative Substrate Succinate
	}, 
	year  = {2007}, 
	journal = {Eng. Life Sci}, 
	volume = {No. 4}, 
	number = {7}, 
	pages  = {331-342}
}
@ARTICLE{Pseudomonas_Veronii, 
	author = {Morales and al., Marian}, 
	title  = {The Genome of the Toluene-Degrading Pseudomonas veronii Strain 1YdBTEX2 and Its Differential Gene Expression in Contaminated Sand.
	}, 
	year  = {2016}, 
	journal = {PLOS ONE}, 
	volume = {November 3}, 
	number = {DOI:10.1371/journal.pone.0165850}, 
	pages  = {1-21}
}

@online{toluene, 
	author = {Scottish Environment Protection Agency}, 
	title = {Pollutant fact sheet : Toluene}, 
	date  = {2017-11	}, 
	url  = {http://apps.sepa.org.uk/spripa/Pages/SubstanceInformation.aspx?pid=89}
}	
\end{filecontents*}

\usepackage[
%backend=biber, 
natbib=true, 
style=numeric, 
sorting=none
]{biblatex}
\addbibresource{\jobname.bib}
\vspace{-2cm}
\title{\LARGE \bf
The Effect of Bacterial Interactions on Fitness
}

\author{Léonard Jequier, Olivier Bützberger, Evan Bexkens and Victor Amstutz% 
}

\begin{document}

\vspace{-2cm}
\maketitle
\thispagestyle{plain}
\pagestyle{plain}
\pagenumbering{arabic}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}

%	One of the crucial objectives after an environmental pollution is to recolonise the area. The first to do that are usually microorganisms, therefore helping them and understand this procedure is one of the important challenges of our time. Using bioaugmentation to help a community regrow is a recent method that can be used to fight against pollution. The two microorganism we chose for our experiment are \textit{Pseudomonas putida} and \textit{Pseudomonas veronii}, as they are able to degrade a widely used hydrocarbonate, toluene. We wanted to know if the addition of one of these strain to a bacterial community extracted from sand would have an effect on the growth of this community. In this experiment we worked with toluene and a sand community extracted from St-Sulpice. Our results are encouraging and would deserve some further experimentations. In the experiment conditions, the final amount of \textit{Pseudomonas} cells was way higher than the Sand Community cells, which means that the overall community was quite different from the starting Sand Community.

In the case of an environmental pollution, the microbial community of the soil will have an important role in the degradation of the pollutant. However, adaptation to the sudden change in the soil composition is difficult for most bacterial communities. Bioaugmentation is a method that could be used to help them overcome the effect of pollution. It's the addition of bacteria able to degrade the pollutant into the contaminated environment. In our experiment, we chose to add \textit{Pseudomonas veronii} and \textit{Pseudomonas putida} to a bacterial community extracted from sand and to grow them either with toluene only or with mixed carbon\textsuperscript{1} substrate. As the two \textit{Pseudomonas} strains we added are able to degrade toluene, we wanted to know if the addition of one of these strain to this bacterial community would have an effect on the growth of this community.
Our results are encouraging and would deserve some further experimentations. However, in the experiment conditions, the final amount of \textit{Pseudomonas} cells was way higher than the Sand Community cells, which means that the overall community was quite different from the starting Sand Community.

\end{abstract}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{INTRODUCTION}
%alternative beginning

%Every surface, soil or liquid in our environment is colonised by multiple microorganisms, interacting with each other and forming communities. However, the whole complexity of the interactions are still today not always fully understood.
%One of the most important part of these communities is that they not only interact with one another but are able to interact with other organisms. These communities can be perturbed by the effects of pollution as spillage of oil or solvent. We decided to

Every surface, soil or liquid in our environment is colonized by multiple microorganisms, interacting with each other and forming communities. However, the whole complexity of the interactions is still today not always fully understood.
In addition, these communities also interact with other organisms and can be perturbed by the effects of pollution as spillage of oil or solvent. We decided to use toluene as a pollutant for this experiment.

Toluene is a solvent widely used in industry nowadays, as a paint solvent or as extraction solvent in the cosmetic industry. Toluene is a monoaromatic volatile molecule which is toxic and ecotoxic\cite{toluene}. 
When such event happens, one way to treat those is the use of bioremediation. There are several different techniques of bioremediation but they all have the same purpose: helping the native community to overcome the effect of pollution and promoting its regrowth. The technique that interested us in this experiment was bioaugmentation, the addition of a microorganism able to degrade the targeted pollutant to a native community, allowing it to grow back \cite{Bioremediation}.

The microorganisms we chose for our experiment were \textit{Pseudomonas putida} (PP) and \textit{Pseudomonas veronii} (PV), both able to metabolize toluene \cite{pseudomonas_putida} \cite{Pseudomonas_Veronii}. The bacterial community on which we tested this procedure was extracted from sand (sand community (SC)collected at St-Sulpice beach, Switzerland).

To measure the number of cells in our culture we used flow cytometry\footnote{Flow cytometer, Novocyte : https://www.aceabio.com/products/nov-ocyte-flow-cytometer/, Nov. 2017}. This technique consists of passing cells one by one through a capillary and hit each cell with a laser. It also allows us to differentiate cells by their fluorescent markers.

%ALTERNATIVE 1

%In our experiment we wanted to know if this ability to metabolize toluene could not only have a positive effect on a native community, for example by lowering the toluene concentration or by producing metabolites that the bacteria from SC could use as carbon source. Our hypothesis for this experiment was that the addition of \textit{Pseudomonas putida} or \textit{Pseudomonas veronii} will have an effect on SC growth, especially in a toluene-only media. 
%ALTERNATIVE 2

%Our hypothesis for this experiment was that the addition of Pseudomonas putida or Pseudomonas veronii will have an effect on SC growth, especially in a toluene-only media.
%Ideed, we think that these Pseudomonas bacteria could produce metabolites the SC bacteria could use as carbon source or reduce the toluene concentration and thus it's toxic effect. This would lead to a better growth of the sand community in presence of one of these pseudomonas strains.

Our hypothesis for this experiment was that the addition of \textit{Pseudomonas putida} or \textit{Pseudomonas veronii} will have an effect on SC growth, especially in a toluene-only media, because we think that these strains might produce metabolites the SC could use as carbon source or reduce the toluene concentration and thus its toxic effect. This would lead to a better growth of the sand community in presence of one of these \textit{Pseudomonas} strains.

\section{MATERIAL AND METHOD}

\subsection{Experimental design}
Apart from SC, we used two bacterial strains : \textit{Pseudomonas veronii} 1YdBTEX2 (tagged with mCherry) and \textit{Pseudomonas putida F1}(also tagged with mCherry).

However, keep in mind that SC isn't a single species of bacteria, but rather a community containing potentially many different species.
%There were 3 bacterial cultures used for this experiment: \textit{Pseudomonas veronii} 1YdBTEX2 (tagged with mCherry, called PV), \textit{Pseudomonas putida F1}(tagged with mCherry, called PP) and a Sand Community, extracted from the beach of St-Sulpice. 
We experimented with two media: a mixed carbon medium\footnote{Mixed Carbon media composition : L-Arginine, D-Xylose, Aspartic acid potassium salt, 2-Hydroxybenzoic acid, L-Phenylalanine, L-Serine, Gamma Hydroxy butyric acid, D-cellobiose, alpha-D-Lactose, Putrescine, Itaconic acid, alpha-D-Glucose-1-phosphate, D-Glucosaminic acid, N-acetyl-D-glucosamine, 4-Hydroxy benzoic acid, D-Mannitol, meso-erytritol, Galacturonic acid, Methyl pyruvate, Tween 20.} and a Minimal Media 1x (MM) with only toluene as carbon source.

We separated the work into two weeks, and tested a different \textit{Pseudomonas} strain each time. In each experiment, we tested 2 species and their interaction in mixed carbon and toluene.

\begin{figure}[H]

		\includegraphics[width=9cm]{erlenmeyer.PNG}
	\caption{Experimental design. Experiments was separated into 2 weeks, with triplicates for each bacterial culture. The number of cells was measured at multiple timepoints.}
	\label{design_weeks}

\end{figure}

As controls, we used SC alone in both media, to prove that the medium has an effect and compare with the interaction of species. PP(or PV) alone in both media are used to show that the medium has no effect.
We therefore had 6 unique conditions, and used 3 replicates for each. In the end, we had 18 cultures per experiment. These cultures were then sampled and counted regularly with a flow cytometer at different timepoints. The timespan between two timepoints had to vary to fit our personal schedule.

\subsection{Extraction of Sand Community (SC)}
The sand came from St-Sulpice. We took 200g of it and mixed it with 400 ml of 1x Minimal Media (MM) in a flask. We blocked the neck, shaked it at 25°C, 115rpm for one hour, the time needed to extract the cells from the sand. The supernatant was collected in 50 ml falcon tubes, then centrifuged at 800rpm for 10 minutes. All the supernatant was then sieved through 40 µm, and centrifuged at 4’000rpm for 30 minutes. The supernatant was discarded, the pellets re-suspended in 5 ml 1x MM. Then centrifuged at 800rpm for 10 minutes. We collected the supernatant, and repeated this step until there was no more visible pellet.

\subsection{Pseudomonas veronii and Pseudomonas putida}
The laboratory's samples were kept at -80°C, taken and streaked on LB plates with antibiotics (Gentamicin GM10). Incubated at 30°C, then streaked one colony on MM 1x plates without added carbon. All the plates were put in a closed chamber containing 200 µl 100\% toluene. The plates were incubated at 30°C. Then took one colony, put on liquid MM with 5 mM succinate, and incubated at 30°C.

\subsection{Inoculation}
We put 20 ml of mixed carbon media in nine flasks, and 20 ml of MM 1x in the other nine, where we added 200 µl toluene 100\% in a tip sealed at the bottom. Toluene being volatile, it will then evaporate and dissolve in the liquid media, it will then be the only source of carbon. We quantified the cells by using the flow cytometer, then calculated to put $10^{6}$ cells/ml in PV/PP alone flasks, SC flasks, and added twice $10^{6}$ cells in PV (or PP) + SC flasks. The flasks containing toluene were sealed to avoid toluene leaks (fig. \ref{flasks}).
They were incubated at 25°C and constantly shaken at 110rpm during 48 hours.

\subsection{Sampling and count of cells}
Every few hours (see fig. \ref{design_weeks} for precise times), we sampled the cells. We took 200 µl from each, and plated it on a 96-well plate. We took 3 samples from each flask, to make technical replicates, and stained them with 4 µl SYTO-9 (50 µM), a  green fluorescent nucleic acid stain\footnote{ref. https://www.thermofisher.com/order/catalog/product/S34854, Nov. 2017}.

To measure the growth of our cells we used a flow cytometer. 
Since the \textit{Pseudomonas} strains were tagged with mCherry (a red fluorescent protein encoded by mcherry gene, inserted downstream of the constitutive promoter of PP strain), and all the cells (both Gram positive and Gram negative cells) were stained with SYTO-9, we could differentiate PP/PV from SC. Also, we had to dilute our samples when the concentration of cell became too high. Otherwise we risked to clog the capillaries.
In the first experiment, we diluted our sample 10 fold at timepoint 1 and 100 fold from timepoint 2. In the second experiment, we diluted our sample 10 fold at timepoints 1 to 4 and 100 fold from timepoint 5.
We then adjusted the results to the original concentration during the analysis. The water in the last 2 rows is used to clean the capillary between samples.
%\begin{figure} 
%	\centering
%	 \raggedright
%	\includegraphics[width=8cm]{96wellplate.jpg}
%	\caption{96 well plate map used in our experiments. The numbers (1, 2, 3) represent the replicates\textsuperscript{*}.}
%	\small\textsuperscript{*} http://www.cellsignet.com/media/plates/96.jpg, Nov. 2017
%	\label{96wellplate}
%  
%\vspace{-0.5cm}	
%\end{figure}

\begin{figure} [H]
	\centering

		\includegraphics[width=8.2cm]{scatterplot.PNG}
		\caption{On the left, the data of unstained sample. On the right, stained samples. Horizontal axis : intensity of red fluorescence. Vertical axis : intensity of green fluorescence.}
		\label{scatterplot}

\end{figure}

We can see on figure \ref{scatterplot} that the \textit{Pseudomonas} cells form a distinct, compact cluster (in red). The limitation between SC (in green) and remaining particles (in black) however, is a bit more subtle to determine. During the second experiment, we had the idea of using an unstained measurement to determine a threshold of green fluorescence value from which we consider the particles to be cells (reminder: as SYTO-9 binds DNA and will stain only cells). We applied these gates to every sample
of both experiments.

\subsection{Statistical method}
Finally, our data was composed of red and green fluorescent cell counts for each treatment, at 4 timepoints every day for two days.\\
We represented graphically the logarithm of these counts over time for each replica and calculated the area under the curve. It allowed to summarize the data to one value per replica of each treatment.
We performed four two-way crossed Anova to test the difference in growth of each Species separately between the substrate. For example, to test the difference in growth of SC in the first experiment, we used: \\
Explicative variables:
\begin{itemize}
	\item Species in culture: SC or SC + PP
	\item Media: Toluene or mixed Carbon
\end{itemize}
Response variable:
\begin{itemize}
	\item Log of the area under the curve
\end{itemize}

\section{RESULTS}
\subsection{Week 1 $\textendash$ SC, PP, PP+SC}
\subsubsection{Total cell count comparison}

First, we were interested in the total cell count of each treatment. We looked at the sum of both fluorescence counts.
In mixed carbon (figure \ref{totcountmixC1}), PP and PPSC curves look very similar. SC seems to grow slower but catch up with the other culture after 40 hours.
In toluene (figure \ref{totcounttol1}), PP and PPSC look again very similar. This time however, 
we don’t observe any growth in the SC culture.
This experiment shows no signs that growing PP and SC together influences the growth of the overall population or the total cell count after 48 hours, in a mixed carbon or toluene media(compared to the PP alone control).
Since the species are marked with different fluorescence, we can also compare the growth of each population separately in each treatment.\newline

\subsubsection{Sand Community}
The growth of the sand community in each treatment for the first experiment is represented in figure \ref{SCgrowth1}.
There is an important interaction between the explicative variables (F = 26.62, df = 1, $p = 8.64\cdot 10 ^{-4}$).
In mixed carbon, SC grows similarly in presence or absence of PP (black and blue curve).
In toluene however, the presence of PP allows for a 1000-fold difference on average (red and yellow curves).
We conclude that the presence of PP affects SC differently depending on the media. In toluene, it allows for a better growth but has no effect in the mix carbon media. In addition, the effect of the media on SC is important in absence of PP. SC alone grows less in toluene than in mixed carbon.\newline
%There is an important difference between the media (F =907.30, df = 1, $p = 2.36 \cdot 10^{-6}$). It is clearly shown on the figure \ref{PPgrowth1} (red and yellow curves vs black and blue curves).
%In contrast, our data shows no significant difference due to the presence or absence of the sand community and no interaction.
%We conclude that SC has no effect on the growth of PP and that PP grows better in toluene only than in mixed carbon. It is certainly due the greater amount of carbon in the toluene media.

\subsubsection{Pseudomonas putida}
There is an important difference between the media (F =907.30, df = 1, $p = 2.36 \cdot 10^{-6}$). It is clearly shown on the figure \ref{PPgrowth1} (red and yellow curves vs black and blue curves).
In contrast, our data shows no significant difference due to the presence or absence of the sand community and no interaction.
We conclude that SC has no effect on the growth of PP and that PP grows better in the Toluene medium than in the mix carbon medium. It is certainly due the greater amount of carbon in the toluene media.

\subsection{Week 2 $\textendash$ SC, PV, PV+SC}

\subsubsection{Total cell count comparison}
The total cell count over time is represented on figure \ref{totcountmixC2} and \ref{totcounttol2}, the conclusion is the same as in the first experiment. It shows no signs that growing PV and SC together influences the growth of the overall population nor the total cell count after 48 hours, in a mixed carbon or toluene media.\newline
\subsubsection{Sand Community}
The growth of the sand community in each treatment for the second experiment is represented in figure \ref{SCgrowth2}.
In contrast with the first experiment, SC was able to grow in toluene. It is not surprising, as a community extracted from sand is typically composed of many kinds of bacteria. It is likely that at least one of them can degrade a given carbon source. But it shows that the sand community we extracted behaved differently from one experiment to another and thus cannot be considered similar. Therefore, we won't be able to compare the results from the two experiments. 
The anova on the area under the curve shows no significant effect of any explicative variables, but we believe the results could be different if we continued the culture for a day because we can see on the growth graph that SC alone is still in exponential growth at 48 hours in toluene. It is plausible that with a few more timepoints, SC would grow higher alone than in presence of PV.\newline

\subsubsection{Pseudomonas veronii}
The growth of the PV in each treatment is represented in figure \ref{PVgrowth2}.
As in the first experiment, there is an important difference of growth between the media (F = 784.71, df = 1, $p = 2.85 \cdot 10^{-9}$). PP grew about a hundred-fold greater in toluene (red and orange) than in mixed carbon (black and blue curves).
One can also notice that PP grew slightly less in presence of SC, in both media (blue and yellow compared to black and red curves). The difference in area under the curve is significant (F = 5.56, df = 1, $p = 0.046$).While not being as significant as our other results, it seems to indicate some competition between them in this type of culture. It seem plausible, knowing from previous experiments that PV grows a bit slower than PP and in this experiment some bacteria from the sand community were able to grow on toluene.
\newline

\section{DISCUSSION}
While these results are promising, further analysis and plotting were carried out to ensure reliability of our results. 
The first drawback of the design we noticed is the proportion of SC cells compared to PP or PV  (fig. \ref{barplot}). We see that the proportion of SC is low compared to the overall population ($\cong 5\%$). This would be a problem in a bioremediation context because the original community was almost completely replaced.

\begin{figure}
	\centering

	\includegraphics[width=8cm]{problem_barplot.PNG}
	\caption{Proportion of red and green fluorescence in the PV + SC and PP + SC cultures in toluene.}
	\label{barplot}

\end{figure}
To solve this problem, we would like to analyse this further by trying different culture conditions. Firstly, we would try to have a mixed carbon with toluene substrate. Secondly, it would be great to vary toluene and carbon concentration. Third and final, we would like our conditions to be as close to reality as possible. For example growing the cells in sand would certainly affect their growth and fitness.

We noticed the second drawback when we plotted the count of SYTO-9 stained cells over time, for PP alone and PP with SC in toluene in figure \ref {problemsyto}.

\begin{figure}

	\begin{subfigure}{.5\textwidth}
		\centering
		\includegraphics[width=8cm]{problemw1.PNG}

		\label{problemw1}
	\end{subfigure}
	\begin{subfigure}{.5\textwidth}
		\centering
		\includegraphics[width=8cm]{problemw2.PNG}

		\label{problemw2}
	\end{subfigure}
\caption{Top figure : Total count of green stained cells in toluene for PP alone and PP with SC during week 1. it showed no significant differences. Bottom figure : Total count of green stained cells in toluene for PV alone and PV with SC during week 2. it showed no significant differences.}
\label{problemsyto}

\end{figure}
The green cells count in PP alone is surprising, knowing that SYTO-9 was used to identify SC cells, while \textit{Pseudomonas putida} was tagged with mCherry, which emits a red fluorescence.

Our hypothesis is that some \textit{Pseudomonas putida} cells died and it stopped their metabolic activities, disabling the mCherry fluorescence. However, if the cells do not lyse, their DNA is still nicely protected and can be stained by SYTO-9. 
The similarity between the two lines hints us that what we considered as SC cells in PP + SC represented in reality mostly dead \textit{Pseudomonas putida} cells and not SC cells.

\subsection{Improvements}

To circumvent this problem, another tagging method unchanged by cell death could be used. For example, a highly specific antibody to \textit{Pseudomonas putida} could be engineered. A secondary antibody, this time linked to a fluorescent protein would bind the first one and therefore mark all \textit{Pseudomonas putida} cells. This would allow a better differentiation of our communities.
\begin{figure}[H]
	\centering

	\includegraphics[width=8.5cm]{antibodytag.jpg}
	\caption{Fluorescent antibody tagging, as an alternative to mCherry in this experiment}
	\label{antibody}

\end{figure}
Another point that could be interesting to change is the initial concentration of PP and PV. Indeed we used $10^{6}$ cells of SC and $10^{6}$ cells of PP or PV. Maybe by reducing the initial concentration of PP/PV we could reduce their competition with SC over resources, and therefore observing a better growth for SC in toluene media.

In addition, we inoculated the media with the same number of PP or PV with SC and haven't considered the fact that SC community is composed of different bacterial species.
The high quantity of a single strain may have made it easier for them  to outgrow SC over time.

%Finally, as often in the lab, our results seem to unveil more questions than answers. We would have liked, if time allowed it, to perform additional experiments proposed above. Because in the present state, we got interesting results, but due to some unforeseeable events, we cannot be certain that they are not artefacts due to the issue differentiating the cells we mentioned before.

Finally, the results of our study open new questions for which we need to perform additional experiments, such as those described above. The issue with this staining technique might carry some artefacts that should be considered in data interpretation.

In conclusion, in the present state, our study shows interesting results. However, the issue with this staining technique might carry some artefacts that should be considered in data interpretation. If time had allowed it, we would have liked to perform the additional experiments proposed above to solve this issue.

%\addtolength{\textheight}{-12cm}  % This command serves to balance the column lengths
                 % on the last page of the document manually. It shortens
                 % the textheight of the last page by a suitable amount.
                 % This command does not take effect until the next page
                 % so it should come on the page before the last. Make
                 % sure that you do not shorten the textheight too much.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section*{Acknowledgments}
Many thanks to Manupriyam Dubey and Andrea Vucicevic for their help in the lab and the design, their presence and support throughout this experiment. We also wish to thank Sara Mitri and Frédéric Schütz for their precious advices.

\printbibliography
\vspace*{\fill}
\textit{APPENDIX A on next page}
\clearpage
APPENDIX A

\begin{figure}[H]

	\includegraphics[width=8.5cm]{flasks.jpg}
	\caption{Flasks of week 1. The ones with the aluminum foil caps contain the mixed carbon medium and are not sealed. The ones with the red cap contain the toluene (see the sealed tip inside) and are sealed to avoid toluene leaks and loss of pollutant.}
	\label{flasks}
\end{figure}
\vspace*{\fill}
\textit{APPENDIX B on next page}
\clearpage

\begin{landscape}

	\begin{figure}
		APPENDIX B

		\flushleft
		\begin{subfigure}{.35\textheight}
			\centering

			\includegraphics[width=6.5cm]{totcount_mixC1.png}
			%	\phantomsubcaption
			\caption{}
			%	\caption{Growth curves of total count in Mixed Carbon, Experiment 1 }

			\label{totcountmixC1}
		\end{subfigure}%
		\begin{subfigure}{.35\textheight}
			\centering

			\includegraphics[width=6.5cm]{totcount_tol1.png}
			%		\phantomsubcaption
			\caption{}
			%		\caption{Growth curves of total count in toluene, Experiment 1 }
			\label{totcounttol1}
		\end{subfigure}%	
		\begin{subfigure}{.35\textheight}
			\centering

			\vspace{-0.1cm}
			\includegraphics[width=6.5cm]{SCgrowth1.png}
			%		\phantomsubcaption
			\caption{}
			%		\caption{SC Growth curves, Experiment 1}
			\label{SCgrowth1}
		\end{subfigure}%
		\begin{subfigure}{.35\textheight}
			\centering
			\vspace{0cm}
			\includegraphics[width=6.5cm, height=4.3cm]{PPgrowth1.png}
			%			\phantomsubcaption
			\caption{}
			%		\caption{PP Growth curves, Experiment 1}
			\label{PPgrowth1}
		\end{subfigure}	
		\begin{subfigure}{.35\textheight}
			\centering

			\includegraphics[width=6.5cm, height=4.65cm]{totcount_mixC2.png}
			%		\phantomsubcaption
			\caption{}
			%		\caption{Growth curves of total count in Mixed Carbon, Experiment 2}
			\label{totcountmixC2}
		\end{subfigure}%
		\begin{subfigure}{.35\textheight}
			\centering

			\includegraphics[width=6.5cm]{totcount_tol2.png}
			%		\phantomsubcaption
			\caption{}
			%		\caption{Growth curves of total count in toluene, Experiment 2}
			\label{totcounttol2}
		\end{subfigure}%	
		\begin{subfigure}{.35\textheight}
			\centering
			\vspace{-0cm}	
			\includegraphics[width=6.5cm]{SCgrowth2.png}
			%		\phantomsubcaption
			\caption{}
			%		\caption{SC Growth curves, Experiment 2}
			\label{SCgrowth2}
		\end{subfigure}%
		\begin{subfigure}{.35\textheight}
			\centering
			\vspace{-0cm}
			\includegraphics[width=6.5cm]{PVgrowth2.png}
			%		\phantomsubcaption
			\caption{}
			%		\caption{PP Growth curves, Experiment 2}
			\label{PVgrowth2}
		\end{subfigure}

		\caption{ Growth curves of: \ref{totcountmixC1}, Total count in Mixed Carbon, Experiment 1; \ref{totcounttol1}, Total count of cells in toluene, Experiment 2; \ref{SCgrowth1}, SC growth in different substrates, Experiment 1; \ref{PPgrowth1}, SC growth in different substrates, Experiment 1;\ref{totcountmixC2}, Total count in Mixed Carbon, Experiment 2; \ref{totcounttol2}, Total count of cells in toluene, Experiment 2; \ref{SCgrowth2}, SC growth in different substrates, Experiment 2; \ref{PVgrowth2}, SC growth in different substrates, Experiment 2.}

	\end{figure}
\end{landscape}

\end{document}

### 2017-12-12 Data_csv/Week1.R
yooooococona

@@ -313,8 +313,9 @@ for(i in 1:8){
 
 #Normal
 par(mfrow = c(1,1))
-plot( cell_count$time, cell_count$MixC_SCmoy_G,log="y",xlim=c(0,48),ylim=c(2950,4028683330), cex.main=1.2,
-     cex.lab=1.2,type="o",main="SC growth\n Experiment 1",xlab= "Time [Hours]", ylab="SC count")
+par(mai = rep(1,4), pin = c(10, 6))
+plot( cell_count$time, cell_count$MixC_SCmoy_G,log="y",xlim=c(0,48),ylim=c(2950,4028683330), cex.main=2.5,cex.axis=1.3,
+     cex.lab=1.7,type="o",main="SC growth\n Experiment 1",xlab= "Time [Hours]", ylab="SC count")
 #replicats
 points( cell_count$time, cell_count$MixC_SC1_G,type = "p")
 points( cell_count$time, cell_count$MixC_SC2_G,type = "p")
@@ -338,7 +339,7 @@ points(cell_count$time,cell_count$Tol_PPSC1_G, type="p", col="orange")
 points(cell_count$time,cell_count$Tol_PPSC2_G, type="p", col="orange")
 points(cell_count$time,cell_count$Tol_PPSC3_G, type="p", col="orange")
 
-legend("topleft", cex=1.2,legend=c("SC alone in mixC","SC alone in Tol","SC in PPSC in mixC","SC in PPSC in Tol"),fill=c("black","red","blue","orange"))
+legend("topleft", cex.2,legend=c("SC alone in mixC","SC alone in Tol","SC in PPSC in mixC","SC in PPSC in Tol"),fill=c("black","red","blue","orange"))
 
 #AIRE COLOREES
 x<-c(0,cell_count$time)
@@ -346,8 +347,8 @@ y <- c(0,cell_count$MixC_SCmoy_G)
 
 xleo = c(0, cell_count$time,48)
 
-plot(x,y,log="y",xlim=c(0,48),cex.main=1.2,
-     cex.lab=1.2,ylim=c(2950,4028683330), type="o",main="SC growth\nWeek1",xlab= "Time [Hours]", ylab="log(SC count)")
+plot(x,y,log="y",xlim=c(0,48),cex.main=2.5,cex.axis=1.3,
[…]

### 2017-12-12 Data_csv/Week2_lech corrigé.R

@@ -2,7 +2,7 @@ rm(list=ls())
 
 
 #charger les données, après avoir fait session, set working directory, to source file location
-path = "Data_W2_csv2/T"
+path = "Data_W2/T"
 List = vector(mode = "list", length = 8) #sorte de liste qui peut contenir des variables
 csv = c()
 for(i in 1:9){
@@ -473,9 +473,10 @@ write.table(ess2, file = "ess2bis.csv", sep = ",")
 
 #Plot des comptes de SC
 par(mfrow = c(1,1))
-plot(cell_count2$time, cell_count2$MixC_SCmoy_G ,cex.main=1.2,
-     cex.lab=1.2,lwd=1.3,log = "y",xlim=c(0,48), ylim=c(2950,4028683330),
-     type = "l",main="SC growth\n Experiment 2 ",xlab= "Time [Hours]", ylab="SC count")
+par(mai = rep(1,4), pin = c(10, 6))
+plot(cell_count2$time, cell_count2$MixC_SCmoy_G ,cex.main=2.5,
+     cex.lab=2.5,lwd=1.3,log = "y",xlim=c(0,48), ylim=c(2950,4028683330),
+     type = "l",main="SC growth\n Week 2 ",xlab= "Time [Hours]", ylab="SC count")
 points(rep(cell_count2$time, times = 3), c(cell_count2$MixC_SC1_G, cell_count2$MixC_SC2_G,
                                            cell_count2$MixC_SC3_G), type = "p" )
 points(cell_count2$time,cell_count2$Tol_SCmoy_G,type="l", col="red",lwd=1.3)
@@ -494,7 +495,7 @@ points(rep(cell_count2$time, times = 3), c(cell_count2$Tol_PVSC1_G, cell_count2$
 #points(cell_count$time, Tol_all_in_pv, type = "o", col = "pink" ,lwd=1.2)#
 
 #
-legend("topleft",legend=c("SC alone in mixC","SC alone in Tol","SC in PV+SC in mixC","SC in PV+SC in Tol"),fill=c("black","red","blue","orange"),cex=1.2)
+legend("topleft",legend=c("SC alone in mixC","SC alone in Tol","SC in PV+SC in mixC","SC in PV+SC in Tol"),fill=c("black","red","blue","orange"),cex=2.2)
[…]

### 2017-12-12 Data_csv/Week1.R
rd

@@ -403,7 +403,7 @@ points(cell_count$time,cell_count$MixC_PPSC3_R, type="p", col="blue")
 
 #points(cell_count$time, cell_count$MixC_PPSCmoy_R + cell_count$MixC_PPSCmoy_G, type="o", col="brown")
 #points(cell_count$time, cell_count$Tol_PPSCmoy_R, type="o", col="gray")
-legend("topleft",cex=1,legend=c("PP alone in mixC","PP alone in Tol","PP in PP+SC in mixC","PP in PP+SC in Tol"),fill=c("black","red","blue","orange"))
+legend("topleft",cex=1,legend=c("PP alone in mixC","PP alone in Tol","PP in PPSC in mixC","PP in PPSC in Tol"),fill=c("black","red","blue","orange"))
 
 
 #estimer l'erreur des réplicats technique 

### 2017-12-12 Data_csv/Week2_lech corrigé.R

@@ -475,7 +475,7 @@ write.table(ess2, file = "ess2bis.csv", sep = ",")
 par(mfrow = c(1,1))
 par(mai = rep(1,4), pin = c(10, 6))
 plot(cell_count2$time, cell_count2$MixC_SCmoy_G ,cex.main=2.5,
-     cex.lab=2.5,lwd=1.3,log = "y",xlim=c(0,48), ylim=c(2950,4028683330),
+     cex.lab=1.7,lwd=1.3,log = "y",xlim=c(0,48), ylim=c(2950,4028683330),
      type = "l",main="SC growth\n Week 2 ",xlab= "Time [Hours]", ylab="SC count")
 points(rep(cell_count2$time, times = 3), c(cell_count2$MixC_SC1_G, cell_count2$MixC_SC2_G,
                                            cell_count2$MixC_SC3_G), type = "p" )
@@ -495,7 +495,7 @@ points(rep(cell_count2$time, times = 3), c(cell_count2$Tol_PVSC1_G, cell_count2$
 #points(cell_count$time, Tol_all_in_pv, type = "o", col = "pink" ,lwd=1.2)#
 
 #
-legend("topleft",legend=c("SC alone in mixC","SC alone in Tol","SC in PV+SC in mixC","SC in PV+SC in Tol"),fill=c("black","red","blue","orange"),cex=2.2)
+legend("topleft",legend=c("SC alone in mixC","SC alone in Tol","SC in PVSC in mixC","SC in PVSC in Tol"),fill=c("black","red","blue","orange"),cex=2.2)
 #legend("bottomright", legend=c("PVSC total in mixC","PVSC total in Tol","total count in pv alone"), fill=c("brown", "gray", "pink"))
 
 
@@ -509,7 +509,7 @@ legend("topleft",legend=c("SC alone in mixC","SC alone in Tol","SC in PV+SC in m
 par(mai = rep(1,4), pin = c(10, 6))
 plot(cell_count2$time, cell_count2$MixC_PVmoy_R ,log="y",lwd=1.3,
      xlim=c(0,48),ylim=c(2950,4028683330), type="l",main="PV growth\n Week 2",xlab= "Time [Hours]", ylab="PV count", cex.main=2.5,
-     cex.lab=2.5)
+     cex.lab=1.7)
 
 
[…]

### 2017-12-12 Data_csv/Paper/paper.tex
yooooococona
pushpushpanier

@@
 \usepackage{rotating}
+\usepackage{color}
+\usepackage{geometry}
 
@@
 \title{\LARGE \bf
-The Effect of Bacterial Interactions on Fitness
+Can a toluene-degrading bacteria improve the growth of a bacterial community in case of toluene pollution ?
 }
@@
 It's the addition of bacteria able to degrade the pollutant into the contaminated environment.
-In our experiment, we chose to add \textit{Pseudomonas veronii} and \textit{Pseudomonas putida} to a bacterial community extracted from sand and to grow them either with toluene only or with mixed carbon\textsuperscript{1} substrate.
+In our experiment, we chose to add \textit{Pseudomonas veronii} 1YdBTEX2 and \textit{Pseudomonas putida F1} (both tagged with fluorescent mCherry protein) to a bacterial community extracted from sand and to grow them either with toluene only or with mixed carbon\textsuperscript{1} substrate.
 As the two \textit{Pseudomonas} strains we added are able to degrade toluene, we wanted to know if the addition of one of these strain to this bacterial community would have an effect on the growth of this community.
 Our results are encouraging and would deserve some further experimentations.
-However, in the experiment conditions, the final amount of \textit{Pseudomonas} cells was way higher than the Sand Community cells, which means that the overall community was quite different from the starting Sand Community.
+However, our results indicate that the Sand Community was almost entirely replaced by \textit{Pseudomonas veronii} or \textit{putida}.
+
+%However, in the experiment conditions, the final amount of \textit{Pseudomonas} cells was way higher than the Sand Community cells, which means that the overall community was quite different from the starting Sand Community.
 
@@
 When such event happens, one way to treat those is the use of bioremediation.
-There are several different techniques of bioremediation but they all have the same purpose: helping the native community to overcome the effect of pollution and promoting its regrowth.
+There are several different techniques of bioremediation but they all have the same purpose: to use live organisms to get rid of pollutants.
 The technique that interested us in this experiment was bioaugmentation, the addition of a microorganism able to degrade the targeted pollutant to a native community, allowing it to grow back \cite{Bioremediation}.
@@
 To measure the growth of our cells we used a flow cytometer. 
-Since the \textit{Pseudomonas} strains were tagged with mCherry (a red fluorescent protein encoded by mcherry gene, inserted downstream of the constitutive promoter of PP strain), and all the cells (both Gram positive and Gram negative cells) were stained with SYTO-9, we could differentiate PP/PV from SC.
-Also, we had to dilute our samples when the concentration of cell became too high.
-Otherwise we risked to clog the capillaries.
-In the first experiment, we diluted our sample 10 fold at timepoint 1 and 100 fold from timepoint 2.
-In the second experiment, we diluted our sample 10 fold at timepoints 1 to 4 and 100 fold from timepoint 5.
-We then adjusted the results to the original concentration during the analysis. The water in the last 2 rows is used to clean the capillary between samples.
+Since \textit{Pseudomonas putida F1} and \textit{Pseudomonas veronii} 1YdBTEX2 were tagged with mCherry (a red fluorescent protein encoded by mcherry gene, inserted downstream of the constitutive promoter of PP strain), and all the cells (both Gram positive and Gram negative cells) were stained with SYTO-9, we could differentiate PP/PV from SC.
 %\begin{figure} 
@@
 
-		\includegraphics[width=8.2cm]{scatterplot.PNG}
-		\caption{On the left, the data of unstained sample. On the right, stained samples. Horizontal axis : intensity of red fluorescence. Vertical axis : intensity of green fluorescence.}
+		\includegraphics[width=9cm]{t8_unstained_ppsc11.PNG}
+		\caption{On the left, the data of unstained sample (unstained PPSC, replicate 1, timepoint 8).
+On the right, stained sample (stained PPSC, replicate 1, timepoint 8).
+Horizontal axis : intensity of red fluorescence.
+Vertical axis : intensity of green fluorescence.}
 		\label{scatterplot}
@@
 
-We can see on figure \ref{scatterplot} that the \textit{Pseudomonas} cells form a distinct, compact cluster (in red).
+On the left side of figure \ref{scatterplot} is a scatter plot of an unstained sample of PPSC.
+On the vertical axis is represented red fluorescence.
+The horizontal axis shows green fluorescence.
+A big black cluster and a red one above it can be observed.
+The black cluster is composed of SC cells and remaining particles.
+They show  low red and green fluorescence values.
+The PP cells express mCherry and therefore show red fluorescence, which causes an upwards shift on the plot, forming the red cluster above.
+
+On the right side of figure \ref{scatterplot} is a scatterplot of a sample from the same culture at the same timepoint but stained with SYTO-9.
+The SYTO-9 binds DNA and stains all the cells (\textit{Pseudomonas} and Sand Community alike) with a green fluorescence, which causes them to shift to the right side.
+However, the red fluorescence value still allows for a distinction between PP/PV and SC.
+The various residual particles (black cluster) are not affected by the SYTO-9.
+
+From the unstained sample, we were able to determine gates (the red and green frames on the scatterplots) to differentiate what we will consider as SC, PP/PV or simply residual sand particles.
+These gates could then be applied to each sample.
+
+Also, we had to dilute our samples when the concentration of cell became too high. Otherwise we risked to clog the capillaries.
+In the first experiment, we diluted our sample 10 fold at timepoint 1 and 100 fold from timepoint 2.
+In the second experiment, we diluted our sample 10 fold at timepoints 1 to 4 and 100 fold from timepoint 5.
+We then adjusted the results to the original concentration during the analysis. The water in the last 2 rows is used to clean the capillary between samples.
+%We can see on figure \ref{scatterplot} that the \textit{Pseudomonas} cells form a distinct, compact cluster (in red).
 The limitation between SC (in green) and remaining particles (in black) however, is a bit more subtle to determine.
-During the second experiment, we had the idea of using an unstained measurement to determine a threshold of green fluorescence value from which we consider the particles to be cells (reminder: as SYTO-9 binds DNA and will stain only cells).
-We applied these gates to every sample
-of both experiments.
+During the second experiment, we used an unstained measurement to determine a threshold of green fluorescence value from which we consider the particles to be cells (reminder: as SYTO-9 binds DNA and will stain only cells).
+We applied these gates to every sample of both experiments.
 
@@
 \clearpage
-
+\newgeometry{bottom=1.5cm,top=1.5cm}
 \begin{landscape}
@@
 		\flushleft
-		\begin{subfigure}{.35\textheight}
+		\begin{subfigure}{.47\textheight}
 			\centering
 
-			\includegraphics[width=6.5cm]{totcount_mixC1.png}
+			\includegraphics[width=7.71cm]{totcount_mixC1.png}
 			%	\phantomsubcaption
@@
 		\end{subfigure}%
-		\begin{subfigure}{.35\textheight}
+		\begin{subfigure}{.47\textheight}
 			\centering
 
-			\includegraphics[width=6.5cm]{totcount_tol1.png}
+			\includegraphics[width=7.71cm]{totcount_tol1.png}
 			%		\phantomsubcaption
@@
 		\end{subfigure}%	
-		\begin{subfigure}{.35\textheight}
+		\begin{subfigure}{.47\textheight}
 			\centering
 
-			\vspace{-0.1cm}
-			\includegraphics[width=6.5cm]{SCgrowth1.png}
+			%\vspace{-0.1cm}
+			\includegraphics[width=7.71cm]{SCgrowth1.png}
 			%		\phantomsubcaption
@@
 		\end{subfigure}%
-		\begin{subfigure}{.35\textheight}
+		\begin{subfigure}{.47\textheight}
 			\centering
 			\vspace{0cm}
-			\includegraphics[width=6.5cm, height=4.3cm]{PPgrowth1.png}
+			\includegraphics[width=7.71cm]{PPgrowth1.png}
 			%			\phantomsubcaption
@@
 		\end{subfigure}	
-		\begin{subfigure}{.35\textheight}
+		\begin{subfigure}{.47\textheight}
 			\centering
 
-			\includegraphics[width=6.5cm, height=4.65cm]{totcount_mixC2.png}
+			\includegraphics[width=7.71cm]{totcount_mixC2.png}
 			%		\phantomsubcaption
@@
 		\end{subfigure}%
-		\begin{subfigure}{.35\textheight}
+		\begin{subfigure}{.47\textheight}
 			\centering
 
-			\includegraphics[width=6.5cm]{totcount_tol2.png}
+			\includegraphics[width=7.71cm]{totcount_tol2.png}
 			%		\phantomsubcaption
@@
 		\end{subfigure}%	
-		\begin{subfigure}{.35\textheight}
+		\begin{subfigure}{.47\textheight}
 			\centering
 			\vspace{-0cm}	
-			\includegraphics[width=6.5cm]{SCgrowth2.png}
+			\includegraphics[width=7.71cm]{SCgrowth2.png}
 			%		\phantomsubcaption
@@
 		\end{subfigure}%
-		\begin{subfigure}{.35\textheight}
+		\begin{subfigure}{.47\textheight}
 			\centering
 			\vspace{-0cm}
-			\includegraphics[width=6.5cm]{PVgrowth2.png}
+			\includegraphics[width=7.71cm]{PVgrowth2.png}
 			%		\phantomsubcaption

### 2017-12-12 Data_csv/Paper/root.tex
pushpushpanier

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%2345678901234567890123456789012345678901234567890123456789012345678901234567890
%        1         2         3         4         5         6         7         8

\documentclass[letterpaper, 10 pt, conference]{ieeeconf}  % Comment this line out if you need a4paper

%\documentclass[a4paper, 10pt, conference]{ieeeconf}      % Use this line for a4 paper

\IEEEoverridecommandlockouts                              % This command is only needed if 
                                                          % you want to use the \thanks command

\overrideIEEEmargins                                      % Needed to meet printer requirements.

% See the \addtolength command later in the file to balance the column lengths
% on the last page of the document

% The following packages can be found on http:\\www.ctan.org
%\usepackage{graphics} % for pdf, bitmapped graphics files
%\usepackage{epsfig} % for postscript graphics files
%\usepackage{mathptmx} % assumes new font selection scheme installed
%\usepackage{times} % assumes new font selection scheme installed
%\usepackage{amsmath} % assumes amsmath package installed
%\usepackage{amssymb}  % assumes amsmath package installed

\title{\LARGE \bf
The Effect of Bacterial Interactions on Fitness
}

\author{Albert Author$^{1}$ and Bernard D. Researcher$^{2}$% <-this % stops a space
\thanks{*This work was not supported by any organization}% <-this % stops a space
\thanks{$^{1}$Albert Author is with Faculty of Electrical Engineering, Mathematics and Computer Science,
        University of Twente, 7500 AE Enschede, The Netherlands
        {\tt\small albert.author@papercept.net}}%
\thanks{$^{2}$Bernard D. Researcheris with the Department of Electrical Engineering, Wright State University,
        Dayton, OH 45435, USA
        {\tt\small b.d.researcher@ieee.org}}%
}

\begin{document}

\maketitle
\thispagestyle{empty}
\pagestyle{empty}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
\textbf{
This electronic document is a live template. The various components of your paper [title, text, heads, etc.] are already defined on the style sheet, as illustrated by the portions given in this document.}

\end{abstract}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{INTRODUCTION}

Mention where mixC comes from and what’s in it
Discussion

While these interactions are promising, further analysis and plotting were carried out to ensure reliability of our results. 
The first drawback of the design  is the proportion of SC cells compared to PP or PV. Considering that 100% of green stained cells are Sand community cells, the count of SC is significantly lower than PP or PV count.  We would like to analyse this further by trying different other culture conditions. Namely, we would first try to have a mixed carbon substrate with toluene. Secondly, it would be great to vary toluene and carbon concentration and observe the effect on fitness. Third and final, we would like our conditions to be as close to reality as possible. Growing the cells in sand could affect their growth and fitness.

The second drawback is observed when plotting the count of SYTO-9 stained cells over time, for P.putida alone and P.putida with the Sand Community in Toluene.

Figure[X] : Green fluorescent cells in Toluene. P.putida alone and P.putida with the Sand Community.

Reminder: SYTO-9 was used to identify SC cells, while P.putida was marked red with m.Cherry
The count green cells in PPalone is therefore surprising. We don’t expect any green fluorescence here. Our hypothesis is that some P.putida cells died and it stopped their metabolic activities, disabling the mCherry fluorescene. However, if the cells do not lyse, their DNA is still nicely protected can be stained by SYTO-9. 
The similarity between the two lines hints us that this count represents mostly dead P.putida cells and not SC cells.

Improvements
To circumvent this problem, another tagging method unchanged by cell death could be used.

For exemple, a highly specific antibody to P.putida could be engineered. A secondary antibody, this time linked to a fluorescent protein would bind the first one and therefore mark all P.putida cells. This would allow for a better differentiation between our communities.

\section{PROCEDURE FOR PAPER SUBMISSION}

\subsection{Selecting a Template (Heading 2)}

First, confirm that you have the correct template for your paper size. This template has been tailored for output on the US-letter paper size. 
It may be used for A4 paper size if the paper size setting is suitably modified.

\subsection{Maintaining the Integrity of the Specifications}

The template is used to format your paper and style the text. All margins, column widths, line spaces, and text fonts are prescribed; please do not alter them. You may note peculiarities. For example, the head margin in this template measures proportionately more than is customary. This measurement and others are deliberate, using specifications that anticipate your paper as one part of the entire proceedings, and not as an independent document. Please do not revise any of the current designations

\section{MATH}

Before you begin to format your paper, first write and save the content as a separate text file. Keep your text and graphic files separate until after the text has been formatted and styled. Do not use hard tabs, and limit use of hard returns to only one return at the end of a paragraph. Do not add any kind of pagination anywhere in the paper. Do not number text heads-the template will do that for you.

Finally, complete content and organizational editing before formatting. Please take note of the following items when proofreading spelling and grammar:

\subsection{Abbreviations and Acronyms} Define abbreviations and acronyms the first time they are used in the text, even after they have been defined in the abstract. Abbreviations such as IEEE, SI, MKS, CGS, sc, dc, and rms do not have to be defined. Do not use abbreviations in the title or heads unless they are unavoidable.

\subsection{Units}

\begin{itemize}

\item Use either SI (MKS) or CGS as primary units. (SI units are encouraged.) English units may be used as secondary units (in parentheses). An exception would be the use of English units as identifiers in trade, such as 3.5-inch disk drive.
\item Avoid combining SI and CGS units, such as current in amperes and magnetic field in oersteds. This often leads to confusion because equations do not balance dimensionally. If you must use mixed units, clearly state the units for each quantity that you use in an equation.
\item Do not mix complete spellings and abbreviations of units: Wb/m2 or webers per square meter, not webers/m2. Spell out units when they appear in text: . . . a few henries, not . . . a few H.
\item Use a zero before decimal points: 0.25, not .25. Use cm3, not cc. (bullet list)

\end{itemize}

\subsection{Equations}

The equations are an exception to the prescribed specifications of this template. You will need to determine whether or not your equation should be typed using either the Times New Roman or the Symbol font (please no other font). To create multileveled equations, it may be necessary to treat the equation as a graphic and insert it into the text after your paper is styled. Number equations consecutively. Equation numbers, within parentheses, are to position flush right, as in (1), using a right tab stop. To make your equations more compact, you may use the solidus ( / ), the exp function, or appropriate exponents. Italicize Roman symbols for quantities and variables, but not Greek symbols. Use a long dash rather than a hyphen for a minus sign. Punctuate equations with commas or periods when they are part of a sentence, as in

$$
\alpha + \beta = \chi \eqno{(1)}
$$

Note that the equation is centered using a center tab stop. Be sure that the symbols in your equation have been defined before or immediately following the equation. Use (1), not Eq. (1) or equation (1), except at the beginning of a sentence: Equation (1) is . . .

\subsection{Some Common Mistakes}
\begin{itemize}

\item The word data is plural, not singular.
\item The subscript for the permeability of vacuum ?0, and other common scientific constants, is zero with subscript formatting, not a lowercase letter o.
\item In American English, commas, semi-/colons, periods, question and exclamation marks are located within quotation marks only when a complete thought or name is cited, such as a title or full quotation. When quotation marks are used, instead of a bold or italic typeface, to highlight a word or phrase, punctuation should appear outside of the quotation marks. A parenthetical phrase or statement at the end of a sentence is punctuated outside of the closing parenthesis (like this). (A parenthetical sentence is punctuated within the parentheses.)
\item A graph within a graph is an inset, not an insert. The word alternatively is preferred to the word alternately (unless you really mean something that alternates).
\item Do not use the word essentially to mean approximately or effectively.
\item In your paper title, if the words that uses can accurately replace the word using, capitalize the u; if not, keep using lower-cased.
\item Be aware of the different meanings of the homophones affect and effect, complement and compliment, discreet and discrete, principal and principle.
\item Do not confuse imply and infer.
\item The prefix non is not a word; it should be joined to the word it modifies, usually without a hyphen.
\item There is no period after the et the Latin abbreviation et al..
\item The abbreviation i.e. means that is, and the abbreviation e.g. means for example.

\end{itemize}

\section{USING THE TEMPLATE}

Use this sample document as your LaTeX source file to create your document. Save this file as {\bf root.tex}. You have to make sure to use the cls file that came with this distribution. If you use a different style file, you cannot expect to get required margins. Note also that when you are creating your out PDF file, the source file is only part of the equation. {\it Your \TeX\ $\rightarrow$ PDF filter determines the output file size. Even if you make all the specifications to output a letter file in the source - if your filter is set to produce A4, you will only get A4 output. }

It is impossible to account for all possible situation, one would encounter using \TeX. If you are using multiple \TeX\ files you must make sure that the ``MAIN`` source file is called root.tex - this is particularly important if your conference is using PaperPlaza's built in \TeX\ to PDF conversion tool.

\subsection{Headings, etc}

Text heads organize the topics on a relational, hierarchical basis. For example, the paper title is the primary text head because all subsequent material relates and elaborates on this one topic. If there are two or more sub-topics, the next level head (uppercase Roman numerals) should be used and, conversely, if there are not at least two sub-topics, then no subheads should be introduced. Styles named Heading 1, Heading 2, Heading 3, and Heading 4 are prescribed.

\subsection{Figures and Tables}

Positioning Figures and Tables: Place figures and tables at the top and bottom of columns. Avoid placing them in the middle of columns. Large figures and tables may span across both columns. Figure captions should be below the figures; table heads should appear above the tables. Insert figures and tables after they are cited in the text. Use the abbreviation
Fig. 1, even at the beginning of a sentence.

\begin{table}[h]
\caption{An Example of a Table}
\label{table_example}
\begin{center}
\begin{tabular}{|c||c|}
\hline
One & Two\\
\hline
Three & Four\\
\hline
\end{tabular}
\end{center}
\end{table}

   \begin{figure}[thpb]
      \centering
      \framebox{\parbox{3in}{We suggest that you use a text box to insert a graphic (which is ideally a 300 dpi TIFF or EPS file, with all fonts embedded) because, in an document, this method is somewhat more stable than directly inserting a picture.
}}
      %\includegraphics[scale=1.0]{figurefile}
      \caption{Inductance of oscillation winding on amorphous
       magnetic core versus DC bias magnetic field}
      \label{figurelabel}
   \end{figure}

Figure Labels: Use 8 point Times New Roman for Figure labels. Use words rather than symbols or abbreviations when writing Figure axis labels to avoid confusing the reader. As an example, write the quantity Magnetization, or Magnetization, M, not just M. If including units in the label, present
them within parentheses. Do not label axes only with units.
In the example, write Magnetization (A/m) or Magnetization {A[m(1)]}, ot just A/m. Do not label axes with a ratio of
quantities and units. For example, write Temperature (K),
not Temperature/K.

\section{CONCLUSIONS}

A conclusion section is not required. Although a conclusion may review the main points of the paper, do not replicate the abstract as the conclusion. A conclusion might elaborate on the importance of the work or suggest applications and extensions.

\addtolength{\textheight}{-12cm}   % This command serves to balance the column lengths
                                  % on the last page of the document manually. It shortens
                                  % the textheight of the last page by a suitable amount.
                                  % This command does not take effect until the next page
                                  % so it should come on the page before the last. Make
                                  % sure that you do not shorten the textheight too much.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{APPENDIX}

Appendixes should appear before the acknowledgment.

\section*{ACKNOWLEDGMENT}

The preferred spelling of the word acknowledgment in America is without an e after the g. Avoid the stilted expression, One of us (R. B. G.) thanks . . . Instead, try R. B. G. thanks. Put sponsor acknowledgments in the unnumbered footnote on the first page.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

References are important to the reader; therefore, each citation must be complete and correct. If at all possible, references should be commonly available publications.

\begin{thebibliography}{99}

\bibitem{c1} G. O. Young, Synthetic structure of industrial plastics (Book style with paper title and editor), in Plastics, 2nd ed. vol. 3, J. Peters, Ed.  New York: McGraw-Hill, 1964, pp. 1564.
\bibitem{c2} W.-K. Chen, Linear Networks and Systems (Book style).	Belmont, CA: Wadsworth, 1993, pp. 123135.
\bibitem{c3} H. Poor, An Introduction to Signal Detection and Estimation.   New York: Springer-Verlag, 1985, ch. 4.
\bibitem{c4} B. Smith, An approach to graphs of linear forms (Unpublished work style), unpublished.
\bibitem{c5} E. H. Miller, A note on reflector arrays (Periodical styleAccepted for publication), IEEE Trans. Antennas Propagat., to be publised.
\bibitem{c6} J. Wang, Fundamentals of erbium-doped fiber amplifiers arrays (Periodical styleSubmitted for publication), IEEE J. Quantum Electron., submitted for publication
\bibitem{c7} C. J. Kaufman, Rocky Mountain Research Lab., Boulder, CO, private communication, May 1995.
\bibitem{c8}  Y. Yorozu, M. Hirano, K. Oka, and Y. Tagawa, Electron spectroscopy studies on magneto-optical media and plastic substrate interfaces(Translation Journals style), IEEE Transl. J. Magn.Jpn., vol. 2, Aug. 1987, pp. 740741 [Dig. 9th Annu. Conf. Magnetics Japan, 1982,
p. 301].
\bibitem{c9} M. Young, The Techincal Writers Handbook.  Mill Valley, CA: University Science, 1989.
\bibitem{c10} J. U. Duncombe, Infrared navigationPart I: An assessment of feasibility (Periodical style), IEEE Trans. Electron Devices, vol. ED-11, pp. 3439, Jan. 1959.
\bibitem{c11} S. Chen, B. Mulgrew, and P. M. Grant, A clustering technique for digital communications channel equalization using radial basis function networks, IEEE Trans. Neural Networks, vol. 4, pp. 570578,
July 1993.
\bibitem{c12} R. W. Lucky, Automatic equalization for digital communication, Bell Syst. Tech. J., vol. 44, no. 4, pp. 547588, Apr. 1965.
\bibitem{c13} S. P. Bingulac, On the compatibility of adaptive controllers (Published Conference Proceedings style), in Proc. 4th Annu. Allerton Conf. Circuits and Systems Theory, New York, 1994, pp. 816.
\bibitem{c14} G. R. Faulhaber, Design of service systems with priority reservation, in Conf. Rec. 1995 IEEE Int. Conf. Communications, pp. 38.
\bibitem{c15} W. D. Doyle, Magnetization reversal in films with biaxial anisotropy, in 1987 Proc. INTERMAG Conf., pp. 2.2-12.2-6.
\bibitem{c16} G. W. Juette and L. E. Zeffanella, Radio noise currents n short sections on bundle conductors (Presented Conference Paper style), presented at the IEEE Summer power Meeting, Dallas, TX, June 2227, 1990, Paper 90 SM 690-0 PWRS
\bibitem{c17}J. G. Kreifeldt, An analysis of surface-detected EMG as an amplitudemodulated noise, presented at the 1989 Int. Conf. Medicine and Biological Engineering, Chicago, IL
\bibitem{c18} J. Williams, Narrow-band analyzer (Thesis or Dissertation style), Ph.D. dissertation, Dept. Elect. Eng., Harvard Univ., Cambridge, MA, 1993.
\bibitem{c19} N. Kawasaki, Parametric study of thermal and chemical nonequilibrium nozzle flow, M.S. thesis, Dept. Electron. Eng., Osaka Univ., Osaka, Japan, 1993.
\bibitem{c20} J. P. Wilkinson, Nonlinear resonant circuit devices (Patent style), U.S. Patent 3 624 12, July 16, 1990.

\end{thebibliography}

\end{document}

### 2017-12-12 Data_csv/Paper/paper.tex
pushiflor

@@
 @ARTICLE{Bioremediation, 
-	author = { Bing Zhao, Chit Laa Poh}, 
-	title  = {“Insights into environmental bioremediation by microorganisms through functional genomics and proteomics”}, 
+	author = { Bing Zhao and Chit Laa Poh}, 
+	title  = {Insights into environmental bioremediation by microorganisms through functional genomics and proteomics}, 
 	year  = {2008}, 
@@
 @ARTICLE{pseudomonas_putida, 
-	author = {Rüegg and al., I.}, 
+	author = {I.Rüegg and 
+		T. Hafner and
+		M. Bucheli-Witschel and
+		T. Egli}, 
 	title  = {Dynamics of Benzene and Toluene Degradation in Pseudomonas putida F1 in the Presence of the Alternative Substrate Succinate
@@
 @ARTICLE{Pseudomonas_Veronii, 
-	author = {Morales and al., Marian}, 
+	author = {Marian Morales and Vladimir Sentchilo and Claire Bertelli and Andrea Komljenovic and Nadezda Kryuchkova-Mostacci and Audrey Bourdilloud and Burkhard Linke and Alexander Goesmann and Keith Harshman and Francisca Segers and Fabien Delapierre and Damien Fiorucci and Mathieu Seppey and Evgeniya Trofimenco and Pauline Berra and Athimed El Taher and Chloé Loiseau and Dejan Roggero and Madeleine Sulfiotti and Angela Etienne and Gustavo Ruiz Buendia and Loïc Pillard and Angelique Escoriza and Roxane Moritz and Cedric Schneider and Esteban Alfonso and Fatma Ben Jeddou and Oliver Selmoni and Gregory Resch and Gilbert Greub and Olivier Emery and Manupriyam Dubey and Trestan Pillonel and Marc Robinson-Rechavi and Jan Roelof van der Meer},
 	title  = {The Genome of the Toluene-Degrading Pseudomonas veronii Strain 1YdBTEX2 and Its Differential Gene Expression in Contaminated Sand.
@@
 	journal = {PLOS ONE}, 
-	volume = {November 3}, 
 	number = {DOI:10.1371/journal.pone.0165850}, 
@@
 }
+
+@ARTICLE{nodrawback, 
+	author = {M.Cunliffe and M.A.Kertesz}, 
+	title = {Effect of Sphingobium yanoikuyae B1 inoculation on bacterial community dynamics and polycyclic aromatic hydrocarbon degradation in aged and freshly PAH-contaminated soils}, 
+	year  = {2006}, 
+	journal = {Environmental Pollution}, 
+	volume = {144}, 
+	number = {1}, 
+	pages  = {228-237}
+}
+
+@ARTICLE{bouchez, 
+	author = {Bouchez and al.}, 
+	title = {Ecological study of a bioaugmentation failure}, 
+	year  = {2000}, 
+	journal = {environmental biology}, 
+	volume = {2}, 
+	number = {2}, 
+	pages  = {179-190}
+}
+
+@ARTICLE{oldarticle, 
+	author = {R.M.Goldstein and L.M.Mallory and M.Alexander}, 
+	title = {Reasons for possible failure of inoculation to enhance biodegradation.}, 
+	year  = {1985}, 
+	journal = {Applied and Environmental Biology}, 
+	volume = {50}, 
+	number = {4}, 
+	pages  = {997-983}
+}
+
 \end{filecontents*}
@@
 
+\newgeometry{left=1.7cm, right=1.7cm, bottom=2cm, top=2cm}
 \vspace{-2cm}
@@
 
-		\includegraphics[width=9cm]{t8_unstained_ppsc11.PNG}
+		\includegraphics[width=8.7cm]{t8_unstained_ppsc11.PNG}
 		\caption{On the left, the data of unstained sample (unstained PPSC, replicate 1, timepoint 8).

### 2017-12-13 Data_csv/Week1.R
iokok

@@ -315,7 +315,7 @@ for(i in 1:8){
 par(mfrow = c(1,1))
 par(mai = rep(1,4), pin = c(10, 6))
 plot( cell_count$time, cell_count$MixC_SCmoy_G,log="y",xlim=c(0,48),ylim=c(2950,4028683330), cex.main=2.5,cex.axis=1.3,
-     cex.lab=1.7,type="o",main="SC growth\n Experiment 1",xlab= "Time [Hours]", ylab="SC count")
+     cex.lab=1.7,type="o",main="SC growth\n Week 1",xlab= "Time [Hours]", ylab="SC count")
 #replicats
 points( cell_count$time, cell_count$MixC_SC1_G,type = "p")
 points( cell_count$time, cell_count$MixC_SC2_G,type = "p")
@@ -339,7 +339,7 @@ points(cell_count$time,cell_count$Tol_PPSC1_G, type="p", col="orange")
 points(cell_count$time,cell_count$Tol_PPSC2_G, type="p", col="orange")
 points(cell_count$time,cell_count$Tol_PPSC3_G, type="p", col="orange")
 
-legend("topleft", cex.2,legend=c("SC alone in mixC","SC alone in Tol","SC in PPSC in mixC","SC in PPSC in Tol"),fill=c("black","red","blue","orange"))
+legend("topleft", cex=1.7,legend=c("SC alone in mixC","SC alone in Tol","SC in PPSC in mixC","SC in PPSC in Tol"),fill=c("black","red","blue","orange"))
 
 #AIRE COLOREES
 x<-c(0,cell_count$time)
@@ -363,7 +363,7 @@ polygon(xleo, yol2, col=rgb(0,0,1,0.4))
 points(cell_count$time,cell_count$Tol_PPSCmoy_G, type="o", col="orange")
 yol3 <- c(100,cell_count$Tol_PPSCmoy_G,100)
 polygon(xleo, yol3, col=rgb(0.8,0.3,0.1,0.4))
-legend("topleft", cex.2,legend=c("SC alone in mixC","SC alone in Tol","SC in PPSC in mixC","SC in PPSC in Tol"),fill=c("black","red","blue","orange"))
+legend("topleft", cex=1.7,legend=c("SC alone in mixC","SC alone in Tol","SC in PPSC in mixC","SC in PPSC in Tol"),fill=c("black","red","blue","orange"))
 
[…]

### 2017-12-13 Data_csv/Week2_lech corrigé.R

@@ -474,7 +474,7 @@ write.table(ess2, file = "ess2bis.csv", sep = ",")
 #Plot des comptes de SC
 par(mfrow = c(1,1))
 par(mai = rep(1,4), pin = c(10, 6))
-plot(cell_count2$time, cell_count2$MixC_SCmoy_G ,cex.main=2.5,
+plot(cell_count2$time, cell_count2$MixC_SCmoy_G ,cex.main=2.5, cex.axis=1.3,
      cex.lab=1.7,lwd=1.3,log = "y",xlim=c(0,48), ylim=c(2950,4028683330),
      type = "l",main="SC growth\n Week 2 ",xlab= "Time [Hours]", ylab="SC count")
 points(rep(cell_count2$time, times = 3), c(cell_count2$MixC_SC1_G, cell_count2$MixC_SC2_G,
@@ -495,7 +495,7 @@ points(rep(cell_count2$time, times = 3), c(cell_count2$Tol_PVSC1_G, cell_count2$
 #points(cell_count$time, Tol_all_in_pv, type = "o", col = "pink" ,lwd=1.2)#
 
 #
-legend("topleft",legend=c("SC alone in mixC","SC alone in Tol","SC in PVSC in mixC","SC in PVSC in Tol"),fill=c("black","red","blue","orange"),cex=2.2)
+legend("topleft",legend=c("SC alone in mixC","SC alone in Tol","SC in PVSC in mixC","SC in PVSC in Tol"),fill=c("black","red","blue","orange"),cex=1.7)
 #legend("bottomright", legend=c("PVSC total in mixC","PVSC total in Tol","total count in pv alone"), fill=c("brown", "gray", "pink"))
 
 
@@ -509,7 +509,7 @@ legend("topleft",legend=c("SC alone in mixC","SC alone in Tol","SC in PVSC in mi
 par(mai = rep(1,4), pin = c(10, 6))
 plot(cell_count2$time, cell_count2$MixC_PVmoy_R ,log="y",lwd=1.3,
      xlim=c(0,48),ylim=c(2950,4028683330), type="l",main="PV growth\n Week 2",xlab= "Time [Hours]", ylab="PV count", cex.main=2.5,
-     cex.lab=1.7)
+     cex.lab=1.7, cex.axis=1.3)
 
 
 points(rep(cell_count2$time,times = 3),c(cell_count2$MixC_PV1_R,cell_count2$MixC_PV2_R,cell_count2$MixC_PV3_R), col = "black")
[…]

### 2017-12-13 Data_csv/Paper/paper.tex
trottinette

@@
 First, we were interested in the total cell count of each treatment. We looked at the sum of both fluorescence counts.
-In mixed carbon (figure \ref{totcountmixC1}), PP and PPSC curves look very similar. SC seems to grow slower but catch up with the other culture after 40 hours.
-In toluene (figure \ref{totcounttol1}), PP and PPSC look again very similar. This time however, 
+In mixed carbon (figure \ref{totcountmixC1text}), PP and PPSC curves look very similar. SC seems to grow slower but catch up with the other culture after 40 hours.
+In toluene (figure \ref{totcounttol1text}), PP and PPSC look again very similar. This time however, 
 we don’t observe any growth in the SC culture.
@@
 Since the species are marked with different fluorescence, we can also compare the growth of each population separately in each treatment.\newline
+
+%\begin{figure}[H]
+%	\centering
+%	
+%	\includegraphics[width=9.3cm]{totcount_mixC1.PNG}
+%	\caption{ADD CAPTION}
+%	\label{totcountmixC1text}
+%\end{figure}
+%\begin{figure}[H]
+%	\centering
+%	
+%	\includegraphics[width=9.3cm]{totcount_tol1.PNG}
+%	\caption{ADD CAPTION}
+%	\label{totcounttol1text}
+%\end{figure}
+\begin{figure}[H]
+
+	\begin{subfigure}{.5\textwidth}
+		\centering
+		\includegraphics[width=9cm]{totcount_mixC1.PNG}
+		\caption{}
+		\label{totcountmixC1text}
+	\end{subfigure}
+	\begin{subfigure}{.5\textwidth}
+		\centering
+		\includegraphics[width=9cm]{totcount_tol1.PNG}
+		\caption{}
+		\label{totcounttol1text}
+	\end{subfigure}
+	\caption{\ref{totcountmixC1text}: Total count (SYTO-9 Count + mCherry count) of SC, PP and PPSC over time in a mixed carbon medium during the first week.
+\ref{totcounttol1text} : Total count (SYTO-9 count + mCherry count) of SC, PP and PPSC over time in a toluene only medium during the first week.}
+	\label{totcount1}
+
+\end{figure}
 
@@
 
+\begin{figure}[H]
+
+	\begin{subfigure}{.5\textwidth}
+		\centering
+		\includegraphics[width=9cm]{totcount_mixC2.PNG}
+		\caption{}
+		\label{totcountmixC2text}
+	\end{subfigure}
+	\begin{subfigure}{.5\textwidth}
+		\centering
+		\includegraphics[width=9cm]{totcount_tol2.PNG}
+		\caption{}		
+		\label{totcounttol2text}
+	\end{subfigure}
+	\caption{\ref{totcountmixC2text}: Total count (SYTO-9 Count + mCherry count) of SC, PV and PVSC over time in a mixed carbon medium during the second week.
+\ref{totcounttol2text} : Total count (SYTO-9 count + mCherry count) of SC, PV and PVSC over time in a toluene only medium during the second week.}
+	\label{totcount2}
+
+\end{figure}
+
 \subsection{Week 2 $\textendash$ SC, PV, PV+SC}
@@
 \subsubsection{Total cell count comparison}
-The total cell count over time is represented on figure \ref{totcountmixC2} and \ref{totcounttol2}, the conclusion is the same as in the first experiment.
+The total cell count over time is represented on figure \ref{totcountmixC2text} and \ref{totcounttol2text}, the conclusion is the same as in the first experiment.
 It shows no signs that growing PV and SC together influences the growth of the overall population nor the total cell count after 48 hours, in a mixed carbon or toluene media.\newline
+
 \subsubsection{Sand Community}
@@
 \section{DISCUSSION}
-While these results are promising, further analysis and plotting were carried out to ensure reliability of our results. 
-The first drawback of the design we noticed is the proportion of SC cells compared to PP or PV  (fig.
+%While these results are promising, further analysis and plotting were carried out to ensure reliability of our results. 
+%The first drawback of the design we noticed is the proportion of SC cells compared to PP or PV  (fig.
 \ref{barplot}).
@@
 
-\begin{figure}
-	\centering
-
-	\includegraphics[width=8cm]{problem_barplot.PNG}
-	\caption{Proportion of red and green fluorescence in the PV + SC and PP + SC cultures in toluene.}
-	\label{barplot}
-
-\end{figure}
-To solve this problem, we would like to analyse this further by trying different culture conditions.
+%\begin{figure}
+%	\centering
+%	 
+%	\includegraphics[width=8cm]{problem_barplot.PNG}
+%	\caption{Proportion of red and green fluorescence in the PV + SC and PP + SC cultures in toluene.}
+%	\label{barplot}
+%	  
+%\end{figure}
+%To solve this problem, we would like to analyse this further by trying different culture conditions.
 Firstly, we would try to have a mixed carbon with toluene substrate.
@@
 
-We noticed the second drawback when we plotted the count of SYTO-9 stained cells over time, for PP alone and PP with SC in toluene in figure \ref {problemsyto}.
+Firstly, in other bioaugmentation experiments, one of the main challenge is the survival of the inoculated strain in presence of a bacterial community \cite{bouchez} \cite{oldarticle}, particularly in absence of pollutant \cite{nodrawback}.
+
+In our experiments, PP and PV were able to grow in both media in presence or absence of SC.
+This led us to think that PP and PV would be interesting candidates for bioaugemtation, especially as they have no problem growing with SC in mixed carbon.
+In addition, it seems that PP has a good growth in presence of SC, while PV has low growth in presence of SC.
+It makes PP a better candidate than PV for bioaugmentation.
+Further experiments would be required to know if this is also true in a sand medium and especially over a longer period of time.
+Similar experiments could also be performed on different native communities.
+Also, it would be interesting to vary the concentration of toluene in these experiments.
+
+We noticed a slight drawback when we plotted the count of SYTO-9 stained cells over time, for PP alone and PP with SC in toluene in figure \ref {problemsyto}.
 
@@
 		\centering
-		\includegraphics[width=8cm]{problemw1.PNG}
+		\includegraphics[width=9cm]{problemw1.PNG}
 
@@
 		\centering
-		\includegraphics[width=8cm]{problemw2.PNG}
+		\includegraphics[width=9cm]{problemw2.PNG}
 
@@
 \end{figure}
-The green cells count in PP alone is surprising, knowing that SYTO-9 was used to identify SC cells, while \textit{Pseudomonas putida} was tagged with mCherry, which emits a red fluorescence.
 
-Our hypothesis is that some \textit{Pseudomonas putida} cells died and it stopped their metabolic activities, disabling the mCherry fluorescence.
+The cell count in the Syto-9 only gate (green frame in fig.
+\ref{scatterplot}) in PP or PV alone is surprising, knowing that both PP and PV were tagged with mCherry, which emits a red fluorescence and causes an upwards shift in the fluorescence graph (as explained in fig.
+\ref{scatterplot}).
+
+Our hypothesis is that some Pseudomonas putida cells died and stopped their metabolic activities, reducing mCherry fluorescence, causing them to appear in the SYTO-9 only gate.
 However, if the cells do not lyse, their DNA is still nicely protected and can be stained by SYTO-9.
-The similarity between the two lines hints us that what we considered as SC cells in PP + SC represented in reality mostly dead \textit{Pseudomonas putida} cells and not SC cells.
+The similarity between the two lines hints us that what we considered as SC cells in PPSC are actually mostly dead \textit{Pseudomonas putida} cells and not SC cells.
 

### 2017-12-13 Data_csv/Week1.R
graphes 4 valeur pour paper à la fin de week 1

@@ -810,3 +810,43 @@ tot_sc_w1_MixC_auc
 
 model_w1_tot = aov()
 
+#graphes AUC paper
+## graphes de l'anova SC semaine 1 seulement 4 valeurs
+par(mfrow = c(1,1))
+par(mai = c(2,1,1,1))
+AUC_col = rep(c("black", "blue", "red","orange"), each = 3)
+plot(rep(1:4, each = 3), log(week$AUC[c(1:3,7:9,16:18, 22:24)]),
+     cex.main=2.5,cex.axis=1.3, 
+     cex.lab=1.7,main = "AUC for each treatment of SC\nWeek 1",
+     xlab = "", xaxt = "n", ylab = "log (AUC)", pch=c(1,3,4), col=AUC_col, ylim = range(log(week$AUC)))
+axis(1, cex=1.7,at = 1:4, labels = c("SC in MixC", "SC in MixC\n in presence of PP ","SC in Tol", "SC in tol\nin presence of PP" ), las = 2, hadj = T, font = 2, outer = F)
+
+plot(rep(1:4, each = 3), log(week$AUC[c(4:6,10:12,19:21, 25:27)]),
+     cex.main=2.5,cex.axis=1.3,
+     cex.lab=1.7,main = "AUC for each treatment of PP\nWeek 1",
+     xlab = "", xaxt = "n", ylab = "log (AUC)", pch=c(1,3,4), col=AUC_col, ylim = range(log(week$AUC)))
+axis(1, cex=1.7,at = 1:4, labels = c("PP in MixC", "PP in MixC\n in presence of SC ","PP in Tol", "PP in tol\nin presence of SC" ), las = 2, hadj = T, font = 2, outer = F)
+
+plot(rep(1:4, each = 3), log(week$AUC[c(1:3,7:9,16:18, 22:24)+30]),
+     cex.main=2.5,cex.axis=1.3,
+     cex.lab=1.7,main = "AUC for each treatment of SC\nWeek 2",
+     xlab = "", xaxt = "n", ylab = "log (AUC)", pch=c(1,3,4), col=AUC_col, ylim = range(log(week$AUC)))
+axis(1, cex=1.7,at = 1:4, labels = c("SC in MixC", "SC in MixC\n in presence of PV ","SC in Tol", "SC in tol\nin presence of PV" ), las = 2, hadj = T, font = 2, outer = F)
+
[…]

### 2017-12-13 Data_csv/Paper/paper.tex
okok

@@
 
+@Manual{R,
+	title = {R: A Language and Environment for Statistical Computing},
+	author = {{R Core Team}},
+	organization = {R Foundation for Statistical Computing},
+	address = {Vienna, Austria},
+	year = {2017},
+	url = {https://www.R-project.org/},
+}
 \end{filecontents*}
@@
 We quantified the cells by using the flow cytometer, then calculated to put $10^{6}$ cells/ml in PV/PP alone flasks, SC flasks, and added twice $10^{6}$ cells in PV (or PP) + SC flasks.
-The flasks containing toluene were sealed to avoid toluene leaks (fig.
+The flasks containing toluene were sealed to avoid toluene leaks (Fig.
 \ref{flasks}).
@@
 \subsection{Sampling and count of cells}
-Every few hours (see fig.
-\ref{design_weeks} for precise times), we sampled the cells.
-We took 200 µl from each, and plated it on a 96-well plate.
-We took 3 samples from each flask, to make technical replicates, and stained them with 4 µl SYTO-9 (50 µM), a  green fluorescent nucleic acid stain\footnote{ref.
+Every few hours (see Fig.
+\ref{design_weeks} for precise times), we took 3 samples from each flask, to make technical replicates, and stained them with 4 µl SYTO-9 (50 µM), a  green fluorescent nucleic acid stain\footnote{ref.
 https://www.thermofisher.com/order/catalog/product/S34854, Nov.
 2017}.
+We then added 200 µl of each sample to the wells of a 96-well plate.
 
@@
 
-\begin{figure} [H]
+\begin{figure}[H]
+	\hspace{-0.3cm}
+	\begin{subfigure}{.25\textwidth}
 		\centering
 
-		\includegraphics[width=8.7cm]{t8_unstained_ppsc11.PNG}
-		\caption{On the left, the data of unstained sample (unstained PPSC, replicate 1, timepoint 8).
-On the right, stained sample (stained PPSC, replicate 1, timepoint 8).
+		\includegraphics[width=4.3cm]{t8_unstained_ppsc1.png}
+		\caption{}
+		\label{scatter1}
+
+	\end{subfigure}%
+	\begin{subfigure}{.22\textwidth}
+		\centering
+
+		\includegraphics[width=4.3cm]{t8_stained_ppsc1.png}
+		\caption{}
+		\label{scatter2}
+
+	\end{subfigure}
+	\caption{\ref{scatter1}: Data of unstained sample (unstained PPSC, replicate 1, timepoint 8).
+\ref{scatter2}: Data of stained sample (stained PPSC, replicate 1, timepoint 8).
 Horizontal axis : intensity of red fluorescence.
@@
 	\label{scatterplot}
-
 \end{figure}	
-
-On the left side of figure \ref{scatterplot} is a scatter plot of an unstained sample of PPSC.
+\vspace{-0.2cm}
+On Fig.
+\ref{scatter1} is a scatter plot of an unstained sample of PPSC.
 On the vertical axis is represented red fluorescence.
@@
 
-On the right side of figure \ref{scatterplot} is a scatterplot of a sample from the same culture at the same timepoint but stained with SYTO-9.
+On Fig.
+\ref{scatter2} is a scatterplot of a sample from the same culture at the same timepoint but stained with SYTO-9.
 The SYTO-9 binds DNA and stains all the cells (\textit{Pseudomonas} and Sand Community alike) with a green fluorescence, which causes them to shift to the right side.
@@
 We then adjusted the results to the original concentration during the analysis. The water in the last 2 rows is used to clean the capillary between samples.
-%We can see on figure \ref{scatterplot} that the \textit{Pseudomonas} cells form a distinct, compact cluster (in red).
+%We can see on Fig.
+\ref{scatterplot} that the \textit{Pseudomonas} cells form a distinct, compact cluster (in red).
 The limitation between SC (in green) and remaining particles (in black) however, is a bit more subtle to determine.
@@
 \subsection{Statistical method}
-Finally, our data was composed of red and green fluorescent cell counts for each treatment, at 4 timepoints every day for two days.\\
+Finally, our data was composed of red and green fluorescent cell counts for each treatment, at 4 timepoints every day for two days. We used R for all the analysis \cite{R}.\\
 We represented graphically the logarithm of these counts over time for each replica and calculated the area under the curve.
@@
 First, we were interested in the total cell count of each treatment. We looked at the sum of both fluorescence counts.
-In mixed carbon (figure \ref{totcountmixC1text}), PP and PPSC curves look very similar. SC seems to grow slower but catch up with the other culture after 40 hours.
-In toluene (figure \ref{totcounttol1text}), PP and PPSC look again very similar. This time however, 
+In mixed carbon (Fig. \ref{totcountmixC1text}), PP and PPSC curves look very similar. SC seems to grow slower but catch up with the other culture after 40 hours.
+In toluene (Fig. \ref{totcounttol1text}), PP and PPSC look again very similar. This time however, 
 we don’t observe any growth in the SC culture.
@@
 \subsubsection{Sand Community}
-The growth of the sand community in each treatment for the first experiment is represented in figure \ref{SCgrowth1}.
+The growth of the sand community in each treatment for the first experiment is represented in Fig. \ref{SCgrowth1}.
 There is an important interaction between the explicative variables (F = 26.62, df = 1, $p = 8.64\cdot 10 ^{-4}$).
@@
 SC alone grows less in toluene than in mixed carbon.\newline
-%There is an important difference between the media (F =907.30, df = 1, $p = 2.36 \cdot 10^{-6}$). It is clearly shown on the figure \ref{PPgrowth1} (red and yellow curves vs black and blue curves).
+%There is an important difference between the media (F =907.30, df = 1, $p = 2.36 \cdot 10^{-6}$). It is clearly shown on the Fig. \ref{PPgrowth1} (red and yellow curves vs black and blue curves).
 %In contrast, our data shows no significant difference due to the presence or absence of the sand community and no interaction.
@@
 \subsubsection{Pseudomonas putida}
-There is an important difference between the media (F =907.30, df = 1, $p = 2.36 \cdot 10^{-6}$). It is clearly shown on the figure \ref{PPgrowth1} (red and yellow curves vs black and blue curves).
+There is an important difference between the media (F =907.30, df = 1, $p = 2.36 \cdot 10^{-6}$). It is clearly shown on the Fig. \ref{PPgrowth1} (red and yellow curves vs black and blue curves).
 In contrast, our data shows no significant difference due to the presence or absence of the sand community and no interaction.
 We conclude that SC has no effect on the growth of PP and that PP grows better in the Toluene medium than in the mix carbon medium.
-It is certainly due the greater amount of carbon in the toluene media.
+It could be due to the greater amount of carbon in the toluene media.
 
@@
 \subsubsection{Total cell count comparison}
-The total cell count over time is represented on figure \ref{totcountmixC2text} and \ref{totcounttol2text}, the conclusion is the same as in the first experiment.
+The total cell count over time is represented on Fig.
+\ref{totcountmixC2text} and \ref{totcounttol2text}, the conclusion is the same as in the first experiment.
 It shows no signs that growing PV and SC together influences the growth of the overall population nor the total cell count after 48 hours, in a mixed carbon or toluene media.\newline
@@
 \subsubsection{Sand Community}
-The growth of the sand community in each treatment for the second experiment is represented in figure \ref{SCgrowth2}.
+The growth of the sand community in each treatment for the second experiment is represented in Fig. \ref{SCgrowth2}.
 In contrast with the first experiment, SC was able to grow in toluene.
@@
 \subsubsection{Pseudomonas veronii}
-The growth of the PV in each treatment is represented in figure \ref{PVgrowth2}.
+The growth of the PV in each treatment is represented in Fig. \ref{PVgrowth2}.
 As in the first experiment, there is an important difference of growth between the media (F = 784.71, df = 1, $p = 2.85 \cdot 10^{-9}$).
@@
 %While these results are promising, further analysis and plotting were carried out to ensure reliability of our results. 
-%The first drawback of the design we noticed is the proportion of SC cells compared to PP or PV  (fig.
+%The first drawback of the design we noticed is the proportion of SC cells compared to PP or PV  (Fig.
 \ref{barplot}).
@@
 In our experiments, PP and PV were able to grow in both media in presence or absence of SC.
-This led us to think that PP and PV would be interesting candidates for bioaugemtation, especially as they have no problem growing with SC in mixed carbon.
+This led us to think that PP and PV would be interesting candidates for bioaugmentation, especially as they have no problem growing with SC in mixed carbon.
 In addition, it seems that PP has a good growth in presence of SC, while PV has low growth in presence of SC.
@@
 
-We noticed a slight drawback when we plotted the count of SYTO-9 stained cells over time, for PP alone and PP with SC in toluene in figure \ref {problemsyto}.
+We noticed a slight drawback when we plotted the count of SYTO-9 stained cells over time, for PP alone and PPSC in toluene in Fig. \ref {problemsyto}.
 
@@
 		\includegraphics[width=9cm]{problemw1.PNG}
-
+		\caption{}
 		\label{problemw1}
@@
 		\includegraphics[width=9cm]{problemw2.PNG}
-
+		\caption{}
 		\label{problemw2}
 	\end{subfigure}
-\caption{Top figure : Total count of green stained cells in toluene for PP alone and PP with SC during week 1.
+
+\caption{\ref{problemw1} : Total count of green stained cells in toluene for PP alone and PP with SC during week 1.
 it showed no significant differences.
-Bottom figure : Total count of green stained cells in toluene for PV alone and PV with SC during week 2.
+\ref{problemw2} : Total count of green stained cells in toluene for PV alone and PV with SC during week 2.
 it showed no significant differences.}
@@
 
-The cell count in the Syto-9 only gate (green frame in fig.
-\ref{scatterplot}) in PP or PV alone is surprising, knowing that both PP and PV were tagged with mCherry, which emits a red fluorescence and causes an upwards shift in the fluorescence graph (as explained in fig.
+ Indeed, the fact that we get a green-only fluorescence in PP and PV alone is surprising, knowing that both PP and PV were tagged with mCherry, which emits a red fluorescence and causes an upwards shift in the fluorescence graph (as explained in Fig.
 \ref{scatterplot}).
+Moreover, the number of green-fluorescent cells in PP or PV alone looks a lot like the number in PPSC or PVSC (Fig.
+\ref{problemsyto}.
+It is even more visible in Fig.\ref{problemflow}; Fig.\ref{problemflow1} is a representation of PP alone in toluene, and Fig.\ref{problemflow2}) of PPSC in toluene.
+These graphs are almost identical, and both show a green-only fluorescence.
 
-Our hypothesis is that some Pseudomonas putida cells died and stopped their metabolic activities, reducing mCherry fluorescence, causing them to appear in the SYTO-9 only gate.
-However, if the cells do not lyse, their DNA is still nicely protected and can be stained by SYTO-9.
-The similarity between the two lines hints us that what we considered as SC cells in PPSC are actually mostly dead \textit{Pseudomonas putida} cells and not SC cells.
+Our hypothesis is that some PP/PV cells died, but weren’t lysed.
+Their DNA being still nicely protected they could be stained by SYTO-9.
+However, their metabolic activities stopped, reducing mCherry fluorescence.
+Without the red tag, these cells would shift downwards and remain in the SYTO-9 only gate and can't be differentiated from the SC cells.
+\begin{figure}
+	\hspace{-0.3cm}
+	\begin{subfigure}{.25\textwidth}
+		\centering
+		\includegraphics[width=4.3cm]{PP3T5.png}
+		\caption{}
+		\label{problemflow1}
+	\end{subfigure}%
+	\begin{subfigure}{.22\textwidth}
+		\centering		
+		\includegraphics[width=4.3cm]{PPSC1T5.png}
+		\caption{}
+		\label{problemflow2}				
+	\end{subfigure}
+\caption{Scatterplot of a stained PP sample(Fig.
+\ref{problemflow1}) besides a stained PPSC sample (Fig.
+\ref{problemflow2}).
+They look very similar.
+A lot of PP seem to have lost mCherry (red) fluorescence and have shifted downwards (Fig.
+\ref{problemflow1}) and look like the supposed SC cells in Fig.
+\ref{problemflow2}.
+}
+\label{problemflow}
+\end{figure}
 
@@
 \begin{figure}[H]
-
 	\includegraphics[width=8.5cm]{flasks.jpg}
@@
 \end{figure}
+
+\begin{figure}[H]
+	\begin{subfigure}{.5\textwidth}
+		\centering
+		\includegraphics[width=9cm]{aucw1.PNG}
+		\caption{}
+		\label{aucw1}
+	\end{subfigure}
+	\begin{subfigure}{.5\textwidth}
+		\centering
+		\includegraphics[width=9cm]{aucw2.PNG}
+		\caption{}
+		\label{aucw2}
+	\end{subfigure}
+\caption{Week 1
+	From left to right: MixC\_SC\_w1:  Sand community in mixed carbon; MixC\_PP: Pseudomonas Putida in mixed carbon; MixC\_PPSC\_SC: Sand community + Pseudomonas Putida in mixed carbon, “SYTO-9” gate; MixC\_PPSC\_PP: Sand community + Pseudomonas Putida in mixed carbon, “mChe + SYTO\_9” gate; MixC\_PPSC\_SC: Sand community + Pseudomonas Putida in mixed carbon, sum of “SYTO-9 “ gate and “mChe + SYTO\_9” gate ;
+	Tol\_SC\_w1:  Sand community in Toluene; Tol\_PP: Pseudomonas Putida in toluene; Tol\_PPSC\_SC: Sand community + Pseudomonas Putida in toluene, “SYTO-9” gate; Tol\_PPSC\_PP: Sand community + Pseudomonas Putida in toluene, “mChe + SYTO\_9” gate; Tol\_PPSC\_SC: Sand community + Pseudomonas Putida in toluene, sum of “SYTO-9 “ gate and “mChe + SYTO\_9” gate
+}
+\end{figure}
+
 \vspace*{\fill}

### 2017-12-13 Data_csv/Week1.R

@@ -571,7 +571,8 @@ plot(rep(1:10, each = 3), log(week$AUC[1:30]),
      xlab = "", xaxt = "n", ylab = "log (AUC)", col = AUC_col_pseudo, pch=c(1,3,4))
 axis(1, cex=1.7,at = 1:10, labels = unique(eti[1:30]), las = 2, hadj = T, font = 2, outer = F,pch = c(1,3,4))
 
-## graphes seulement 4 valeurs
+
+## graphes seulement 4 valeurs week 2
 par(mai = c(2,1,1,1))
 AUC_col = rep(c("black", "blue", "red","orange"), each = 3)
 plot(rep(1:4, each = 3), log(week$AUC[c(4:6,10:12,19:21, 25:27)]),
@@ -611,13 +612,21 @@ TukeyHSD(modelw1_PP)
 # t.test(week1$AUC[week1$names3=="Tol_PP"], week1$AUC[week1$names3=="Tol_PPSC_PP"])
 #   
 
+#GRAPH AUC WEEK 1
+par(mai = c(2,1,1,1))
+plot(rep(1:10, each = 3), log(week$AUC[1:30]),
+     cex.main=2.5,cex.axis=1.3, ylim = c(15.5, 25),
+     cex.lab=1.7,main = "Area under the curve according to the treatment\n Week 1",
+     xlab = "", xaxt = "n", ylab = "log (AUC)", pch=c(1,3,4))
+axis(1, cex.axis=1.4,at = 1:10, labels = unique(eti[1:30]), las = 2, hadj = T, font = 2, outer = F)
 
+#GRAPH AUC WEEK 2
 #----------------week2
 #graphes week 2 SC
-par(mai = rep(1,4), pin = c(10, 6))
+par(mai = c(2,1,1,1))
 plot(rep(1:10, each = 3), log(week$AUC[31:60]),
      main = "Area under the curve according to the treatment\n Week 2",
-     cex.main=2.5,cex.axis=1.3,
+     cex.main=2.5,cex.axis=1.3, ylim = c(15.5, 25),
      cex.lab=1.7, xlab = "", xaxt = "n", ylab = "log (AUC)", pch = c(1,3,4))
 axis(1, cex.axis=1.4,at = 1:10, labels = unique(eti[31:60]), las = 2, hadj = T, font = 2, outer = F)
 

### 2017-12-13 Data_csv/Paper/paper.tex
tracteur

@@
 Bioaugmentation is a method that could be used to help them overcome the effect of pollution.
-It's the addition of bacteria able to degrade the pollutant into the contaminated environment.
+It is the addition of bacteria able to degrade the pollutant into the contaminated environment.
 In our experiment, we chose to add \textit{Pseudomonas veronii} 1YdBTEX2 and \textit{Pseudomonas putida F1} (both tagged with fluorescent mCherry protein) to a bacterial community extracted from sand and to grow them either with toluene only or with mixed carbon\textsuperscript{1} substrate.
@@
 
-To measure the number of cells in our culture we used flow cytometry\footnote{Flow cytometer, Novocyte : https://www.aceabio.com/products/nov-ocyte-flow-cytometer/, Nov.
+To measure the number of cells in our culture we used flow cytometry\footnote{Flow cytometer, Novocyte : https://www.aceabio.com/products/nov\linebreak[0]ocyte-flow-cytometer/, Nov.
 2017}.
@@
 %There were 3 bacterial cultures used for this experiment: \textit{Pseudomonas veronii} 1YdBTEX2 (tagged with mCherry, called PV), \textit{Pseudomonas putida F1}(tagged with mCherry, called PP) and a Sand Community, extracted from the beach of St-Sulpice.
-We experimented with two media: a mixed carbon medium\footnote{Mixed Carbon media composition : L-Arginine, D-Xylose, Aspartic acid potassium salt, 2-Hydroxybenzoic acid, L-Phenylalanine, L-Serine, Gamma Hydroxy butyric acid, D-cellobiose, alpha-D-Lactose, Putrescine, Itaconic acid, alpha-D-Glucose-1-phosphate, D-Glucosaminic acid, N-acetyl-D-glucosamine, 4-Hydroxy benzoic acid, D-Mannitol, meso-erytritol, Galacturonic acid, Methyl pyruvate, Tween 20.} and a Minimal Media 1x (MM) with only toluene as carbon source.
+We experimented with two media: a mixed carbon medium\footnote{Mixed Carbon media composition : L-Arginine, D-Xylose, Aspartic acid potassium salt, 2-Hydroxybenzoic acid, L-Phenylalanine, L-Serine, Gamma Hydroxy butyric acid, D-cellobiose, alpha-D-Lactose, Putrescine, Itaconic acid, alpha-D-Glucose-1-phosphate, D-Glucosaminic acid, N-acetyl-D-glucosamine, 4-Hydroxy benzoic acid, D-Mannitol, meso-erytritol, Galacturonic acid, Methyl pyruvate, Tween 20.
+Each component in equal concentration} and a Minimal Media 1x (MM) with only toluene as carbon source.
 
@@
 		\includegraphics[width=9cm]{erlenmeyer.PNG}
-	\caption{Experimental design. Experiments was separated into 2 weeks, with triplicates for each bacterial culture. The number of cells was measured at multiple timepoints.}
+	\caption{Experimental design. Experiments were separated into 2 weeks, with triplicates for each bacterial culture. The number of cells was measured at multiple timepoints.}
 	\label{design_weeks}
@@
 PP(or PV) alone in both media are used to show that the medium has no effect.
-We therefore had 6 unique conditions, and used 3 replicates for each.
+We therefore had 6 unique treatments, and used 3 replicates for each.
 In the end, we had 18 cultures per experiment.
@@
 The sand came from St-Sulpice.
-We took 200g of it and mixed it with 400 ml of 1x Minimal Media (MM) in a flask.
+We took 200g of it and mixed it with 400 mL of 1x Minimal Media (MM) in a flask.
 We blocked the neck, shaked it at 25°C, 115rpm for one hour, the time needed to extract the cells from the sand.
-The supernatant was collected in 50 ml falcon tubes, then centrifuged at 800rpm for 10 minutes.
+The supernatant was collected in 50 mL falcon tubes, then centrifuged at 800rpm for 10 minutes.
 All the supernatant was then sieved through 40 µm, and centrifuged at 4’000rpm for 30 minutes.
-The supernatant was discarded, the pellets re-suspended in 5 ml 1x MM.
+The supernatant was discarded, the pellets re-suspended in 5 mL 1x MM.
 Then centrifuged at 800rpm for 10 minutes.
@@
 Incubated at 30°C, then streaked one colony on MM 1x plates without added carbon.
-All the plates were put in a closed chamber containing 200 µl 100\% toluene.
+All the plates were put in a closed chamber containing 200 µL 100\% toluene.
 The plates were incubated at 30°C.
@@
 \subsection{Inoculation}
-We put 20 ml of mixed carbon media in nine flasks, and 20 ml of MM 1x in the other nine, where we added 200 µl toluene 100\% in a tip sealed at the bottom.
-Toluene being volatile, it will then evaporate and dissolve in the liquid media, it will then be the only source of carbon.
-We quantified the cells by using the flow cytometer, then calculated to put $10^{6}$ cells/ml in PV/PP alone flasks, SC flasks, and added twice $10^{6}$ cells in PV (or PP) + SC flasks.
+We put 20 mL of mixed carbon media [0.1mM] in nine flasks, and 20 mL of MM 1x in the other nine, where we added 200 µL toluene  50\% (100 µL toluene and 100 µL 2,2,4,4,6,8,8-Heptamethylnonane (HMN)\footnote{Oil used with volatile solvent to decrease their toxicity by slowing it's release in the medium.
+Ref.
+https://www.sigmaaldrich.com/catalog/product/aldrich/128511?lang\linebreak[0]=fr\&region=CH, Dec.
+2017}) in a tip sealed at the bottom.
+Toluene being volatile, it will then evaporate and dissolve in the liquid media.
+It will then be the only source of carbon.
+We quantified the cells by using flow cytometry, and calculated to put $10^{6}$ cells/mL in PV/PP alone flasks, SC flasks, and added twice $10^{6}$ cells in PPSC and PVSC flasks.
 The flasks containing toluene were sealed to avoid toluene leaks (Fig.
@@
 Every few hours (see Fig.
-\ref{design_weeks} for precise times), we took 3 samples from each flask, to make technical replicates, and stained them with 4 µl SYTO-9 (50 µM), a  green fluorescent nucleic acid stain\footnote{ref.
+\ref{design_weeks} for precise times), we took 3 samples from each flask, to make technical replicates, and stained them with 4 µL SYTO-9 (50 µM), a  green fluorescent nucleic acid stain\footnote{ref.
 https://www.thermofisher.com/order/catalog/product/S34854, Nov.
 2017}.
-We then added 200 µl of each sample to the wells of a 96-well plate.
+We then added 200 µL of each sample to the wells of a 96-well plate.
 
 To measure the growth of our cells we used a flow cytometer. 
-Since \textit{Pseudomonas putida F1} and \textit{Pseudomonas veronii} 1YdBTEX2 were tagged with mCherry (a red fluorescent protein encoded by mcherry gene, inserted downstream of the constitutive promoter of PP strain), and all the cells (both Gram positive and Gram negative cells) were stained with SYTO-9, we could differentiate PP/PV from SC.
+Since \textit{Pseudomonas putida F1} and \textit{Pseudomonas veronii} 1YdBTEX2 were tagged with mCherry (a red fluorescent protein encoded by mCherry gene, inserted downstream of the constitutive promoter of PP strain), and all the cells (both Gram positive and Gram negative cells) were stained with SYTO-9, we could differentiate PP/PV from SC.
 %\begin{figure} 
@@
 	\end{subfigure}
-	\caption{\ref{scatter1}: Data of unstained sample (unstained PPSC, replicate 1, timepoint 8).
+	\caption{Fig.
+\ref{scatter1}: Data of unstained sample (unstained PPSC, replicate 1, timepoint 8).
+Fig.
 \ref{scatter2}: Data of stained sample (stained PPSC, replicate 1, timepoint 8).
@@
 Also, we had to dilute our samples when the concentration of cell became too high. Otherwise we risked to clog the capillaries.
-In the first experiment, we diluted our sample 10 fold at timepoint 1 and 100 fold from timepoint 2.
-In the second experiment, we diluted our sample 10 fold at timepoints 1 to 4 and 100 fold from timepoint 5.
-We then adjusted the results to the original concentration during the analysis. The water in the last 2 rows is used to clean the capillary between samples.
+In the first week, we diluted our sample 10 fold at timepoint 1 and 100 fold from timepoint 2. In the second week, we diluted our sample 10 fold at timepoints 1 to 4 and 100 fold from timepoint 5.
+We then adjusted the results to the original concentration during the analysis. 
 %We can see on Fig.
@@
 The limitation between SC (in green) and remaining particles (in black) however, is a bit more subtle to determine.
-During the second experiment, we used an unstained measurement to determine a threshold of green fluorescence value from which we consider the particles to be cells (reminder: as SYTO-9 binds DNA and will stain only cells).
-We applied these gates to every sample of both experiments.
+During the second week, we used an unstained measurement to determine a threshold of green fluorescence value from which we consider the particles to be cells (reminder: as SYTO-9 binds DNA and will stain only cells).
+We applied these gates to every sample of both weeks.
 
@@
 We performed four two-way crossed Anova to test the difference in growth of each Species separately between the substrate.
-For example, to test the difference in growth of SC in the first experiment, we used: \\
+For example, to test the difference in growth of SC in the first week, we used: \\
 Explicative variables:
@@
 	\item Species in culture: SC or SC + PP
-	\item Media: Toluene or mixed Carbon
+	\item Media: Toluene or mixed carbon
 \end{itemize}
@@
 \section{RESULTS}
-\subsection{Week 1 $\textendash$ SC, PP, PP+SC}
+\subsection{Week 1 $\textendash$ SC, PP, PPSC}
 \subsubsection{Total cell count comparison}
@@
 we don’t observe any growth in the SC culture.
-This experiment shows no signs that growing PP and SC together influences the growth of the overall population or the total cell count after 48 hours, in a mixed carbon or toluene media(compared to the PP alone control).
+This experiment shows no signs that growing PP and SC together influences the growth of the overall population or the total cell count after 48 hours, in a mixed carbon or toluene media (compared to the PP alone control).
 Since the species are marked with different fluorescence, we can also compare the growth of each population separately in each treatment.\newline
@@
 	\end{subfigure}
-	\caption{\ref{totcountmixC1text}: Total count (SYTO-9 Count + mCherry count) of SC, PP and PPSC over time in a mixed carbon medium during the first week.
+	\caption{Fig.
+\ref{totcountmixC1text}: Total count (SYTO-9 Count + mCherry count) of SC, PP and PPSC over time in a mixed carbon medium during the first week.
+Fig.
 \ref{totcounttol1text} : Total count (SYTO-9 count + mCherry count) of SC, PP and PPSC over time in a toluene only medium during the first week.}
@@
 \subsubsection{Sand Community}
-The growth of the sand community in each treatment for the first experiment is represented in Fig. \ref{SCgrowth1}.
+The growth of the sand community in each treatment for the first week is represented in Fig. \ref{SCgrowth1}.
 There is an important interaction between the explicative variables (F = 26.62, df = 1, $p = 8.64\cdot 10 ^{-4}$).
@@
 	\end{subfigure}
-	\caption{\ref{totcountmixC2text}: Total count (SYTO-9 Count + mCherry count) of SC, PV and PVSC over time in a mixed carbon medium during the second week.
+	\caption{Fig.
+\ref{totcountmixC2text}: Total count (SYTO-9 Count + mCherry count) of SC, PV and PVSC over time in a mixed carbon medium during the second week.
+Fig.
 \ref{totcounttol2text} : Total count (SYTO-9 count + mCherry count) of SC, PV and PVSC over time in a toluene only medium during the second week.}
@@
 
-\subsection{Week 2 $\textendash$ SC, PV, PV+SC}
+\subsection{Week 2 $\textendash$ SC, PV, PVSC}
 
@@
 The total cell count over time is represented on Fig.
-\ref{totcountmixC2text} and \ref{totcounttol2text}, the conclusion is the same as in the first experiment.
+\ref{totcountmixC2text} and \ref{totcounttol2text}, the conclusion is the same as in the first week.
 It shows no signs that growing PV and SC together influences the growth of the overall population nor the total cell count after 48 hours, in a mixed carbon or toluene media.\newline
@@
 \subsubsection{Sand Community}
-The growth of the sand community in each treatment for the second experiment is represented in Fig. \ref{SCgrowth2}.
-In contrast with the first experiment, SC was able to grow in toluene.
+The growth of the sand community in each treatment for the second week is represented in Fig. \ref{SCgrowth2}.
+In contrast with the first week, SC was able to grow in toluene.
 It is not surprising, as a community extracted from sand is typically composed of many kinds of bacteria.
 It is likely that at least one of them can degrade a given carbon source.
-But it shows that the sand community we extracted behaved differently from one experiment to another and thus cannot be considered similar.
-Therefore, we won't be able to compare the results from the two experiments.
+But it shows that the sand community we extracted behaved differently from one week to another and thus cannot be considered similar.
+Therefore, we won't be able to compare the results from the two weeks.
 The anova on the area under the curve shows no significant effect of any explicative variables, but we believe the results could be different if we continued the culture for a day because we can see on the growth graph that SC alone is still in exponential growth at 48 hours in toluene.
@@
 The growth of the PV in each treatment is represented in Fig. \ref{PVgrowth2}.
-As in the first experiment, there is an important difference of growth between the media (F = 784.71, df = 1, $p = 2.85 \cdot 10^{-9}$).
+As in the first week, there is an important difference of growth between the media (F = 784.71, df = 1, $p = 2.85 \cdot 10^{-9}$).
 PP grew about a hundred-fold greater in toluene (red and orange) than in mixed carbon (black and blue curves).
@@
 The difference in area under the curve is significant (F = 5.56, df = 1, $p = 0.046$).While not being as significant as our other results, it seems to indicate some competition between them in this type of culture.
-It seem plausible, knowing from previous experiments that PV grows a bit slower than PP and in this experiment some bacteria from the sand community were able to grow on toluene.
+It seems plausible, knowing from previous experiments that PV grows a bit slower than PP and in this experiment some bacteria from the sand community were able to grow on toluene.
 \newline
@@
 
-Firstly, in other bioaugmentation experiments, one of the main challenge is the survival of the inoculated strain in presence of a bacterial community \cite{bouchez} \cite{oldarticle}, particularly in absence of pollutant \cite{nodrawback}.
+Firstly, in other bioaugmentation experiments, one of the main challenges is the survival of the inoculated strain in presence of a bacterial community \cite{bouchez} \cite{oldarticle}, particularly in absence of pollutant \cite{nodrawback}.
 
@@
 
-\caption{\ref{problemw1} : Total count of green stained cells in toluene for PP alone and PP with SC during week 1.
-it showed no significant differences.
+\caption{Fig.
+\ref{problemw1} : Total count of green stained cells in toluene for PP alone and PP with SC during week 1.
+It showed no significant differences.
+Fig.
 \ref{problemw2} : Total count of green stained cells in toluene for PV alone and PV with SC during week 2.
-it showed no significant differences.}
+It showed no significant differences.}
 \label{problemsyto}
@@
 Indeed we used $10^{6}$ cells of SC and $10^{6}$ cells of PP or PV.
-Maybe by reducing the initial concentration of PP/PV we could reduce their competition with SC over resources, and therefore observing a better growth for SC in toluene media.
+Maybe by reducing the initial concentration of PP/PV, we could reduce their competition with SC over resources, and therefore observe a better growth for SC in toluene media.
 
@@
 Because in the present state, we got interesting results, but due to some unforeseeable events, we cannot be certain that they are not artefacts due to the issue differentiating the cells we mentioned before.
-
-Finally, the results of our study open new questions for which we need to perform additional experiments, such as those described above.
+%
+%Finally, the results of our study open new questions for which we need to perform additional experiments, such as those described above.
 The issue with this staining technique might carry some artefacts that should be considered in data interpretation.
@@
 
-		\caption{ Growth curves of: \ref{totcountmixC1}, Total count in Mixed Carbon, Experiment 1; \ref{totcounttol1}, Total count of cells in toluene, Experiment 2; \ref{SCgrowth1}, SC growth in different substrates, Experiment 1; \ref{PPgrowth1}, SC growth in different substrates, Experiment 1;\ref{totcountmixC2}, Total count in Mixed Carbon, Experiment 2; \ref{totcounttol2}, Total count of cells in toluene, Experiment 2; \ref{SCgrowth2}, SC growth in different substrates, Experiment 2; \ref{PVgrowth2}, SC growth in different substrates, Experiment 2.}
+		\caption{ Growth curves of: Fig.
+\ref{totcountmixC1}, Total count in Mixed Carbon, Week 1; Fig.
+\ref{totcounttol1}, Total count of cells in toluene, Week 2; Fig.
+\ref{SCgrowth1}, SC growth in different substrates, Week 1; Fig.
+\ref{PPgrowth1}, SC growth in different substrates, Week 1; Fig.
+\ref{totcountmixC2}, Total count in Mixed Carbon, Week 2; Fig.
+\ref{totcounttol2}, Total count of cells in toluene, Week 2; Fig.
+\ref{SCgrowth2}, SC growth in different substrates, Week 2; Fig.
+\ref{PVgrowth2}, SC growth in different substrates, Week 2.}
 

### 2017-12-13 Data_csv/Week1.R

@@ -524,7 +524,7 @@ plot(rep(1:4, each = 3), log(week$AUC[c(1:3,7:9,16:18, 22:24)]),
      cex.main=2.5,cex.axis=1.3,
      cex.lab=1.7,main = "Area under the curve according to the treatment\nSC Experiment 1",
      xlab = "", xaxt = "n", ylab = "log (AUC)", pch=c(1,3,4), col=AUC_col, ylim = range(log(week$AUC)))
-axis(1, cex=1.7,at = 1:4, labels = c("SC in MixC", "SC in MixC\n in presence of PP ","SC in Tol", "SC in tol\nin presence of PP" ), las = 2, hadj = T, font = 2, outer = F)
+axis(1, cex=1.7,at = 1:4, labels = c("SC in MixC", "SC in MixC in \npresence of PP ","SC in Tol", "SC in tol\nin presence of PP" ), las = 2, hadj = T, font = 2, outer = F)
 #effect de pp in tol
 abline(h = mean(log(week$AUC[c(22:24)])))
 abline(h = mean(log(week$AUC[c(16:18)])))
@@ -579,7 +579,7 @@ plot(rep(1:4, each = 3), log(week$AUC[c(4:6,10:12,19:21, 25:27)]),
      cex.main=2.5,cex.axis=1.3,
      cex.lab=1.7,main = "Area under the curve according to the treatment\n PP Experiment 1",
      xlab = "", xaxt = "n", ylab = "log (AUC)", pch=c(1,3,4), col=AUC_col, ylim = range(log(week$AUC)))
-axis(1, cex=1.7,at = 1:4, labels = c("PP in MixC", "PP in MixC\n in presence of SC ","PP in Tol", "PP in tol\nin presence of SC" ), las = 2, hadj = T, font = 2, outer = F)
+axis(1, cex=1.7,at = 1:4, labels = c("PP in MixC", "PP in MixC in \npresence of SC ","PP in Tol", "PP in tol\nin presence of SC" ), las = 2, hadj = T, font = 2, outer = F)
 
 
 ## test week 1 PP 
@@ -638,7 +638,7 @@ plot(rep(1:4, each = 3), log(week$AUC[c(1:3,7:9,16:18, 22:24)+30]),
      cex.main=2.5,cex.axis=1.3,
      cex.lab=1.7,main = "Area under the curve according to the treatment\nSC Experiment 2",
[…]

### 2017-12-13 Data_csv/paper.tex
ready to read folks !

--- 2017-12-13 Data_csv/Paper/paper.tex
@@
 \title{\LARGE \bf
-Can a toluene-degrading bacteria improve the growth of a bacterial community in case of toluene pollution ?
+Can a toluene-degrading bacteria improve the growth of a bacterial community in case of toluene pollution?
 }
@@
 
-Toluene is a solvent widely used in industry nowadays, as a paint solvent or as extraction solvent in the cosmetic industry.
+Toluene is an organic solvent widely used in industry nowadays, as a paint solvent or as extraction solvent in the cosmetic industry.
 Toluene is a monoaromatic volatile molecule which is toxic and ecotoxic\cite{toluene}.
@@
 The microorganisms we chose for our experiment were \textit{Pseudomonas putida} (PP) and \textit{Pseudomonas veronii} (PV), both able to metabolize toluene \cite{pseudomonas_putida} \cite{Pseudomonas_Veronii}.
-The bacterial community on which we tested this procedure was extracted from sand (sand community (SC)collected at St-Sulpice beach, Switzerland).
+The bacterial community on which we tested this procedure was extracted from sand (sand community (SC) collected at St-Sulpice beach, Switzerland).
 
@@
 \subsection{Inoculation}
-We put 20 mL of mixed carbon media [0.1mM] in nine flasks, and 20 mL of MM 1x in the other nine, where we added 200 µL toluene  50\% (100 µL toluene and 100 µL 2,2,4,4,6,8,8-Heptamethylnonane (HMN)\footnote{Oil used with volatile solvent to decrease their toxicity by slowing it's release in the medium.
+We put 20 mL of mixed carbon media [0.1mM] in nine flasks, and 20 mL of MM 1x in the other nine, where we added 200 µL toluene  50\% (100 µL toluene and 100 µL 2,2,4,4,6,8,8-Heptamethylnonane (HMN)\footnote{Oil used with volatile solvent to decrease their toxicity by slowing its release in the medium.
 Ref.
@@
 
-\begin{figure}[H]
+\begin{figure}
 	\hspace{-0.3cm}
@@
 \end{figure}
-\vspace{-0.2cm}
+
 On Fig.
@@
 %\end{figure}
-\begin{figure}[H]
-
-	\begin{subfigure}{.5\textwidth}
-		\centering
-		\includegraphics[width=9cm]{totcount_mixC1.PNG}
-		\caption{}
-		\label{totcountmixC1text}
-	\end{subfigure}
-	\begin{subfigure}{.5\textwidth}
-		\centering
-		\includegraphics[width=9cm]{totcount_tol1.PNG}
-		\caption{}
-		\label{totcounttol1text}
-	\end{subfigure}
-	\caption{Fig.
+%\begin{figure}[H]
+%	
+%	\begin{subfigure}{.5\textwidth}
+%		\centering
+%		\includegraphics[width=9cm]{totcount_mixC1.PNG}
+%		\caption{}
+%		\label{totcountmixC1text}
+%	\end{subfigure}
+%	\begin{subfigure}{.5\textwidth}
+%		\centering
+%		\includegraphics[width=9cm]{totcount_tol1.PNG}
+%		\caption{}
+%		\label{totcounttol1text}
+%	\end{subfigure}
+%	\caption{Fig.
 \ref{totcountmixC1text}: Total count (SYTO-9 Count + mCherry count) of SC, PP and PPSC over time in a mixed carbon medium during the first week.
@@
 \ref{totcounttol1text} : Total count (SYTO-9 count + mCherry count) of SC, PP and PPSC over time in a toluene only medium during the first week.}
-	\label{totcount1}
+%	\label{totcount1}
+%\end{figure}
 
+\begin{figure}
+	\centering
+	\includegraphics[width=9cm]{totcount_mixC1.PNG}
+	\caption{Total count (SYTO-9 Count + mCherry count) of SC, PP and PPSC over time in a mixed carbon medium during the first week.}
+	\label{totcountmixC1text}
+\end{figure}
+
+\begin{figure}
+	\centering
+	\includegraphics[width=9cm]{totcount_tol1.PNG}
+	\caption{Total count (SYTO-9 count + mCherry count) of SC, PP and PPSC over time in a toluene only medium during the first week.}
+	\label{totcounttol1text}
 \end{figure}
@@
 %We conclude that SC has no effect on the growth of PP and that PP grows better in toluene only than in mixed carbon. It is certainly due the greater amount of carbon in the toluene media.
+\begin{figure}[H]
+	\centering
+	\includegraphics[width=9cm]{AUCsc1.png}
+	\caption{AUC Week 1 SC}
+	\label{aucscw1}
+\end{figure}
+
+\begin{figure}[H]
+	\centering
+	\includegraphics[width=9cm]{AUCpp1.png}
+	\caption{AUC Week 1 PP}
+	\label{aucppw1}
+\end{figure}
 
@@
 
-\begin{figure}[H]
-
-	\begin{subfigure}{.5\textwidth}
-		\centering
-		\includegraphics[width=9cm]{totcount_mixC2.PNG}
-		\caption{}
-		\label{totcountmixC2text}
-	\end{subfigure}
-	\begin{subfigure}{.5\textwidth}
-		\centering
-		\includegraphics[width=9cm]{totcount_tol2.PNG}
-		\caption{}		
-		\label{totcounttol2text}
-	\end{subfigure}
-	\caption{Fig.
+%\begin{figure}[H]
+%	
+%	\begin{subfigure}{.5\textwidth}
+%		\centering
+%		\includegraphics[width=9cm]{totcount_mixC2.PNG}
+%		\caption{}
+%		\label{totcountmixC2text}
+%	\end{subfigure}
+%	\begin{subfigure}{.5\textwidth}
+%		\centering
+%		\includegraphics[width=9cm]{totcount_tol2.PNG}
+%		\caption{}		
+%		\label{totcounttol2text}
+%	\end{subfigure}
+%	\caption{Fig.
 \ref{totcountmixC2text}: Total count (SYTO-9 Count + mCherry count) of SC, PV and PVSC over time in a mixed carbon medium during the second week.
@@
 \ref{totcounttol2text} : Total count (SYTO-9 count + mCherry count) of SC, PV and PVSC over time in a toluene only medium during the second week.}
-	\label{totcount2}
-
-\end{figure}
+%	\label{totcount2}
+%	
+%\end{figure}
 
@@
 
+\begin{figure}[H]
+	\centering
+	\includegraphics[width=9cm]{totcount_mixC2.PNG}
+	\caption{Total count (SYTO-9 Count + mCherry count) of SC, PV and PVSC over time in a mixed carbon medium during the second week.}
+	\label{totcountmixC2text}
+\end{figure}
+
+\begin{figure}[H]
+	\centering
+	\includegraphics[width=9cm]{totcount_tol2.PNG}
+	\caption{Total count (SYTO-9 count + mCherry count) of SC, PV and PVSC over time in a toluene only medium during the second week.}
+	\label{totcounttol2text}
+\end{figure}
 \subsubsection{Sand Community}
@@
 \newline
+
+\begin{figure}[H]
+	\centering
+	\includegraphics[width=9cm]{AUCsc2.png}
+	\caption{AUC Week 2 SC}
+	\label{aucscw2}
+\end{figure}
+
+\begin{figure}[H]
+	\centering
+	\includegraphics[width=9cm]{AUCpv2.png}
+	\caption{AUC Week 2 PV}
+	\label{aucppw2}
+\end{figure}
 
@@
 
-We noticed a slight drawback when we plotted the count of SYTO-9 stained cells over time, for PP alone and PPSC in toluene in Fig. \ref {problemsyto}.
+We noticed a slight drawback when we plotted the count of SYTO-9 stained cells over time, for PP alone and PPSC in toluene in Fig. \ref{problemw1} and \ref{problemw2}.
 
@@
 
-	\begin{subfigure}{.5\textwidth}
 		\centering
 		\includegraphics[width=9cm]{problemw1.PNG}
-		\caption{}
+		\caption{Total count of green stained cells in toluene for PP alone and PP with SC during week 1. It showed no significant differences.}
 		\label{problemw1}
-	\end{subfigure}
-	\begin{subfigure}{.5\textwidth}
+\end{figure}
+
+\begin{figure}
 		\centering
 		\includegraphics[width=9cm]{problemw2.PNG}
-		\caption{}
+		\caption{Total count of green stained cells in toluene for PV alone and PV with SC during week 2. It showed no significant differences.}
 		\label{problemw2}
-	\end{subfigure}
 
-\caption{Fig.
+%\caption{Fig.
 \ref{problemw1} : Total count of green stained cells in toluene for PP alone and PP with SC during week 1.
@@
 It showed no significant differences.}
-\label{problemsyto}
+%\label{problemsyto}
 
@@
 
-\begin{figure}[H]
-	\begin{subfigure}{.5\textwidth}
-		\centering
-		\includegraphics[width=9cm]{aucw1.PNG}
-		\caption{}
-		\label{aucw1}
-	\end{subfigure}
-	\begin{subfigure}{.5\textwidth}
-		\centering
-		\includegraphics[width=9cm]{aucw2.PNG}
-		\caption{}
-		\label{aucw2}
-	\end{subfigure}
-\caption{Week 1
-	From left to right: MixC\_SC\_w1:  Sand community in mixed carbon; MixC\_PP: Pseudomonas Putida in mixed carbon; MixC\_PPSC\_SC: Sand community + Pseudomonas Putida in mixed carbon, “SYTO-9” gate; MixC\_PPSC\_PP: Sand community + Pseudomonas Putida in mixed carbon, “mChe + SYTO\_9” gate; MixC\_PPSC\_SC: Sand community + Pseudomonas Putida in mixed carbon, sum of “SYTO-9 “ gate and “mChe + SYTO\_9” gate ;
-	Tol\_SC\_w1:  Sand community in Toluene; Tol\_PP: Pseudomonas Putida in toluene; Tol\_PPSC\_SC: Sand community + Pseudomonas Putida in toluene, “SYTO-9” gate; Tol\_PPSC\_PP: Sand community + Pseudomonas Putida in toluene, “mChe + SYTO\_9” gate; Tol\_PPSC\_SC: Sand community + Pseudomonas Putida in toluene, sum of “SYTO-9 “ gate and “mChe + SYTO\_9” gate
-}
-\end{figure}
-
 \vspace*{\fill}

### 2017-12-13 Data_csv/Week1.R
fichiers r a jour

@@ -314,8 +314,8 @@ for(i in 1:8){
 #Normal
 par(mfrow = c(1,1))
 par(mai = rep(1,4), pin = c(10, 6))
-plot( cell_count$time, cell_count$MixC_SCmoy_G,log="y",xlim=c(0,48),ylim=c(2950,4028683330), cex.main=2.5,cex.axis=1.3,
-     cex.lab=1.7,type="o",main="SC growth\n Week 1",xlab= "Time [Hours]", ylab="SC count")
+plot( cell_count$time, cell_count$MixC_SCmoy_G,log="y",xlim=c(0,48),ylim=c(2950,4028683330), cex.main=2.5,cex.axis=1.5,
+     cex.lab=2.2,type="o",main="SC growth\n Week 1",xlab= "Time [Hours]", ylab="SC count")
 #replicats
 points( cell_count$time, cell_count$MixC_SC1_G,type = "p")
 points( cell_count$time, cell_count$MixC_SC2_G,type = "p")
@@ -339,7 +339,7 @@ points(cell_count$time,cell_count$Tol_PPSC1_G, type="p", col="orange")
 points(cell_count$time,cell_count$Tol_PPSC2_G, type="p", col="orange")
 points(cell_count$time,cell_count$Tol_PPSC3_G, type="p", col="orange")
 
-legend("topleft", cex=1.7,legend=c("SC alone in mixC","SC alone in Tol","SC in PPSC in mixC","SC in PPSC in Tol"),fill=c("black","red","blue","orange"))
+legend("topleft", cex=2,legend=c("SC alone in mixC","SC alone in Tol","SC in PPSC in mixC","SC in PPSC in Tol"),fill=c("black","red","blue","orange"))
 
 #AIRE COLOREES
 x<-c(0,cell_count$time)
@@ -347,8 +347,8 @@ y <- c(0,cell_count$MixC_SCmoy_G)
 
 xleo = c(0, cell_count$time,48)
 
-plot(x,y,log="y",xlim=c(0,48),cex.main=2.5,cex.axis=1.3,
-     cex.lab=1.7,ylim=c(2950,4028683330), type="o",main="SC growth\nWeek1",xlab= "Time [Hours]", ylab="log(SC count)")
+plot(x,y,log="y",xlim=c(0,48),cex.main=2.5,cex.axis=1.5,
+     cex.lab=2.2,ylim=c(2950,4028683330), type="o",main="SC growth\nWeek1",xlab= "Time [Hours]", ylab="log(SC count)")
[…]

### 2017-12-13 Data_csv/Week2_lech corrigé.R

@@ -474,8 +474,8 @@ write.table(ess2, file = "ess2bis.csv", sep = ",")
 #Plot des comptes de SC
 par(mfrow = c(1,1))
 par(mai = rep(1,4), pin = c(10, 6))
-plot(cell_count2$time, cell_count2$MixC_SCmoy_G ,cex.main=2.5, cex.axis=1.3,
-     cex.lab=1.7,lwd=1.3,log = "y",xlim=c(0,48), ylim=c(2950,4028683330),
+plot(cell_count2$time, cell_count2$MixC_SCmoy_G ,cex.main=2.5, cex.axis=1.5,
+     cex.lab=2.2,lwd=1.3,log = "y",xlim=c(0,48), ylim=c(2950,4028683330),
      type = "l",main="SC growth\n Week 2 ",xlab= "Time [Hours]", ylab="SC count")
 points(rep(cell_count2$time, times = 3), c(cell_count2$MixC_SC1_G, cell_count2$MixC_SC2_G,
                                            cell_count2$MixC_SC3_G), type = "p" )
@@ -495,7 +495,7 @@ points(rep(cell_count2$time, times = 3), c(cell_count2$Tol_PVSC1_G, cell_count2$
 #points(cell_count$time, Tol_all_in_pv, type = "o", col = "pink" ,lwd=1.2)#
 
 #
-legend("topleft",legend=c("SC alone in mixC","SC alone in Tol","SC in PVSC in mixC","SC in PVSC in Tol"),fill=c("black","red","blue","orange"),cex=1.7)
+legend("topleft",legend=c("SC alone in mixC","SC alone in Tol","SC in PVSC in mixC","SC in PVSC in Tol"),fill=c("black","red","blue","orange"),cex=2)
 #legend("bottomright", legend=c("PVSC total in mixC","PVSC total in Tol","total count in pv alone"), fill=c("brown", "gray", "pink"))
 
 
@@ -509,7 +509,7 @@ legend("topleft",legend=c("SC alone in mixC","SC alone in Tol","SC in PVSC in mi
 par(mai = rep(1,4), pin = c(10, 6))
 plot(cell_count2$time, cell_count2$MixC_PVmoy_R ,log="y",lwd=1.3,
      xlim=c(0,48),ylim=c(2950,4028683330), type="l",main="PV growth\n Week 2",xlab= "Time [Hours]", ylab="PV count", cex.main=2.5,
[…]

### 2017-12-13 Data_csv/Paper/paper.tex
push

@@
 
-\begin{figure}[H]
-	\hspace{-0.3cm}
-	\begin{subfigure}{.25\textwidth}
+\begin{figure}
+
+	\begin{minipage}{.48\linewidth}
+	%	\hspace{-0.3cm}
+	%	\begin{subfigure}{.25\textwidth}
 			\centering
 
-		\includegraphics[width=4.3cm]{t8_unstained_ppsc1.png}
-		\caption{}
+			\includegraphics[width=1\linewidth]{t8_unstained_ppsc1.png}
+			\captionof{figure}{Data of unstained sample (unstained PPSC, replicate 1, timepoint 8). Horizontal axis : intensity of red fluorescence. Vertical axis : intensity of green fluorescence.}
 			\label{scatter1}
 
-	\end{subfigure}%
-	\begin{subfigure}{.22\textwidth}
+	%	\end{subfigure}%
+	%	\begin{subfigure}{.22\textwidth}
+	\end{minipage}\hspace{.2cm}
+	\begin{minipage}{.48\linewidth}
+
 			\centering
 
-		\includegraphics[width=4.3cm]{t8_stained_ppsc1.png}
-		\caption{}
+			\includegraphics[width=1\linewidth]{t8_stained_ppsc1.png}
+			\captionof{figure}{Data of stained sample (stained PPSC, replicate 1, timepoint 8). Horizontal axis : intensity of red fluorescence. Vertical axis : intensity of green fluorescence.}
 			\label{scatter2}
 
-	\end{subfigure}
-	\caption{Fig.
+	%	\end{subfigure}
+	%	\caption{Fig.
 \ref{scatter1}: Data of unstained sample (unstained PPSC, replicate 1, timepoint 8).
@@
 Vertical axis : intensity of green fluorescence.}
-	\label{scatterplot}
+	%	\label{scatterplot}
+	\end{minipage}
+
 \end{figure}
-\vspace{-0.2cm}
+
 On Fig.

### 2017-12-14 Data_csv/Paper/paper.tex
My corrections

@@
 It is the addition of bacteria able to degrade the pollutant into the contaminated environment.
-In our experiment, we chose to add \textit{Pseudomonas veronii} 1YdBTEX2 and \textit{Pseudomonas putida F1} (both tagged with fluorescent mCherry protein) to a bacterial community extracted from sand and to grow them either with toluene only or with mixed carbon\textsuperscript{1} substrate.
+In our experiment, we chose to add \textit{Pseudomonas veronii} 1YdBTEX2 and \textit{Pseudomonas putida F1} (both tagged with fluorescent mCherry protein) to a bacterial community extracted from sand and to grow them either with toluene only or with mixed carbon\footnote{Mixed Carbon media composition : L-Arginine, D-Xylose, Aspartic acid potassium salt, 2-Hydroxybenzoic acid, L-Phenylalanine, L-Serine, Gamma Hydroxy butyric acid, D-cellobiose, alpha-D-Lactose, Putrescine, Itaconic acid, alpha-D-Glucose-1-phosphate, D-Glucosaminic acid, N-acetyl-D-glucosamine, 4-Hydroxy benzoic acid, D-Mannitol, meso-erytritol, Galacturonic acid, Methyl pyruvate, Tween 20.
+Each component in equal concentration} substrate.
 As the two \textit{Pseudomonas} strains we added are able to degrade toluene, we wanted to know if the addition of one of these strain to this bacterial community would have an effect on the growth of this community.
@@
 However, the whole complexity of the interactions is still today not always fully understood.
-In addition, these communities also interact with other organisms and can be perturbed by the effects of pollution as spillage of oil or solvent.
+In addition, these communities also interact with other organisms and can be perturbed by the effects of pollution such as spillage of oil or solvent.
 We decided to use toluene as a pollutant for this experiment.
@@
 Toluene is an organic solvent widely used in industry nowadays, as a paint solvent or as extraction solvent in the cosmetic industry.
-Toluene is a monoaromatic volatile molecule which is toxic and ecotoxic\cite{toluene}.
-When such event happens, one way to treat those is the use of bioremediation.
+Toluene is a monoaromatic volatile molecule which is toxic and ecotoxic \cite{toluene}.
+When such event happens, one way to treat it is the use of bioremediation.
 There are several different techniques of bioremediation but they all have the same purpose: to use live organisms to get rid of pollutants.
@@
 
-The microorganisms we chose for our experiment were \textit{Pseudomonas putida} (PP) and \textit{Pseudomonas veronii} (PV), both able to metabolize toluene \cite{pseudomonas_putida} \cite{Pseudomonas_Veronii}.
+The microorganisms we chose for our experiment were \textit{Pseudomonas putida} F1 (PP) and \textit{Pseudomonas veronii} 1YdBTEX2 (PV), both able to metabolize toluene \cite{pseudomonas_putida} \cite{Pseudomonas_Veronii}.
 The bacterial community on which we tested this procedure was extracted from sand (sand community (SC) collected at St-Sulpice beach, Switzerland).
@@
 
-Our hypothesis for this experiment was that the addition of \textit{Pseudomonas putida} or \textit{Pseudomonas veronii} will have an effect on SC growth, especially in a toluene-only media, because we think that these strains might produce metabolites the SC could use as carbon source or reduce the toluene concentration and thus its toxic effect.
+Our hypothesis for this experiment were that the addition of \textit{Pseudomonas putida} or \textit{Pseudomonas veronii} will have an effect on SC growth, especially in a toluene-only media, because we think that these strains might produce metabolites the SC could use as carbon source or reduce the toluene concentration and thus its toxic effect.
 This would lead to a better growth of the sand community in presence of one of these \textit{Pseudomonas} strains.
@@
 %There were 3 bacterial cultures used for this experiment: \textit{Pseudomonas veronii} 1YdBTEX2 (tagged with mCherry, called PV), \textit{Pseudomonas putida F1}(tagged with mCherry, called PP) and a Sand Community, extracted from the beach of St-Sulpice.
-We experimented with two media: a mixed carbon medium\footnote{Mixed Carbon media composition : L-Arginine, D-Xylose, Aspartic acid potassium salt, 2-Hydroxybenzoic acid, L-Phenylalanine, L-Serine, Gamma Hydroxy butyric acid, D-cellobiose, alpha-D-Lactose, Putrescine, Itaconic acid, alpha-D-Glucose-1-phosphate, D-Glucosaminic acid, N-acetyl-D-glucosamine, 4-Hydroxy benzoic acid, D-Mannitol, meso-erytritol, Galacturonic acid, Methyl pyruvate, Tween 20.
-Each component in equal concentration} and a Minimal Media 1x (MM) with only toluene as carbon source.
+We experimented with two media: a mixed carbon medium\textsuperscript{1} and a Minimal Media 1x (MM) with only toluene as carbon source.
 
@@
 We therefore had 6 unique treatments, and used 3 replicates for each.
-In the end, we had 18 cultures per experiment.
+We ended up with 18 cultures per experiment.
 These cultures were then sampled and counted regularly with a flow cytometer at different timepoints.
-The timespan between two timepoints had to vary to fit our personal schedule.
+The timespan between two timepoints had to vary to fit our personal schedules.
 
@@
 We took 200g of it and mixed it with 400 mL of 1x Minimal Media (MM) in a flask.
-We blocked the neck, shaked it at 25°C, 115rpm for one hour, the time needed to extract the cells from the sand.
+We shaked it at 25°C, 115rpm for one hour, the time needed to extract the cells from the sand.
 The supernatant was collected in 50 mL falcon tubes, then centrifuged at 800rpm for 10 minutes.
-All the supernatant was then sieved through 40 µm, and centrifuged at 4’000rpm for 30 minutes.
-The supernatant was discarded, the pellets re-suspended in 5 mL 1x MM.
+All the supernatant was then sieved through a 40 µm filter, and centrifuged at 4’000rpm for 30 minutes.
+The supernatant was discarded and the pellets re-suspended in 5 mL 1x MM.
 Then centrifuged at 800rpm for 10 minutes.
-We collected the supernatant, and repeated this step until there was no more visible pellet.
+We collected the supernatant and repeated this step until there was no visible pellet.
 
 \subsection{Pseudomonas veronii and Pseudomonas putida}
-The laboratory's samples were kept at -80°C, taken and streaked on LB plates with antibiotics (Gentamicin GM10).
-Incubated at 30°C, then streaked one colony on MM 1x plates without added carbon.
+The laboratory's samples were kept at -80°C, taken out at room temperature and streaked on LB plates with antibiotics (Gentamicin GM10).
+Incubated at 30°C, then one colony was streaked on MM 1x plates without added carbon.
 All the plates were put in a closed chamber containing 200 µL 100\% toluene.
 The plates were incubated at 30°C.
-Then took one colony, put on liquid MM with 5 mM succinate, and incubated at 30°C.
+Then took one colony, put it in liquid MM with 5 mM succinate, and incubated it at 30°C.
 
@@
 It will then be the only source of carbon.
-We quantified the cells by using flow cytometry, and calculated to put $10^{6}$ cells/mL in PV/PP alone flasks, SC flasks, and added twice $10^{6}$ cells in PPSC and PVSC flasks.
+We quantified the cells using flow cytometry, and calculated to put $10^{6}$ cells/mL in PV/PP alone flasks, SC flasks, and added twice $10^{6}$ cells in PPSC and PVSC flasks.
 The flasks containing toluene were sealed to avoid toluene leaks (Fig.
@@
 Every few hours (see Fig.
-\ref{design_weeks} for precise times), we took 3 samples from each flask, to make technical replicates, and stained them with 4 µL SYTO-9 (50 µM), a  green fluorescent nucleic acid stain\footnote{ref.
+\ref{design_weeks} for precise times), we took 2 samples from each flask to make technical replicates, and stained them with 4 µL SYTO-9 (50 µM), a  green fluorescent nucleic acid stain\footnote{ref.
 https://www.thermofisher.com/order/catalog/product/S34854, Nov.
@@
 \subsection{Statistical method}
-Finally, our data was composed of red and green fluorescent cell counts for each treatment, at 4 timepoints every day for two days. We used R for all the analysis \cite{R}.\\
+Finally, our data was composed of red and green fluorescent cell counts for each treatment, at 4 timepoints every day for two days. We used the R environment for all the analysis \cite{R}.\\
 We represented graphically the logarithm of these counts over time for each replica and calculated the area under the curve.
-It allowed to summarize the data to one value per replica of each treatment.
+It allowed to summarize the data to one value per replica of each treatment (Fig.
+\ref{aucscw1}, \ref{aucppw1}, \ref{aucscw2}, \ref{aucpvw2}).
 We performed four two-way crossed Anova to test the difference in growth of each Species separately between the substrate.
@@
 
-First, we were interested in the total cell count of each treatment. We looked at the sum of both fluorescence counts.
+First, we are interested in the total cell count of each treatment. We look at the sum of both fluorescence counts.
 In mixed carbon (Fig. \ref{totcountmixC1text}), PP and PPSC curves look very similar. SC seems to grow slower but catch up with the other culture after 40 hours.
@@
 	\includegraphics[width=9cm]{AUCsc1.png}
-	\caption{AUC Week 1 SC}
+	\caption{Week 1 - SC : AUC (Area Under the Curve). Each point represents the mean of the 2 technical replicates.}
 	\label{aucscw1}
@@
 	\includegraphics[width=9cm]{AUCpp1.png}
-	\caption{AUC Week 1 PP}
+	\caption{Week 2 - PP : AUC (Area Under the Curve). Each point represents the mean of the 2 technical replicates.}
 	\label{aucppw1}
@@
 The anova on the area under the curve shows no significant effect of any explicative variables, but we believe the results could be different if we continued the culture for a day because we can see on the growth graph that SC alone is still in exponential growth at 48 hours in toluene.
-It is plausible that with a few more timepoints, SC would grow higher alone than in presence of PV.\newline
+It is plausible that with a few more timepoints, SC would grow better alone than in presence of PV.\newline
 
@@
 	\includegraphics[width=9cm]{AUCsc2.png}
-	\caption{AUC Week 2 SC}
+	\caption{Week 2 - SC : AUC (Area Under the Curve). Each point represents the mean of the 2 technical replicates.}
 	\label{aucscw2}
@@
 	\includegraphics[width=9cm]{AUCpv2.png}
-	\caption{AUC Week 2 PV}
+	\caption{Week 2 - PV : AUC (Area Under the Curve). Each point represents the mean of the 2 technical replicates.}
 	\label{aucppw2}
@@
 \ref{scatterplot}).
-Moreover, the number of green-fluorescent cells in PP or PV alone looks a lot like the number in PPSC or PVSC (Fig.
-\ref{problemsyto}.
+Moreover, the number of green-fluorescent cells in PP or PV alone looks a lot like the number in PPSC (Fig.
+\ref{problemw1}) or PVSC (Fig.
+\ref{problemw2}).
+
 It is even more visible in Fig.\ref{problemflow}; Fig.\ref{problemflow1} is a representation of PP alone in toluene, and Fig.\ref{problemflow2}) of PPSC in toluene.
@@
 
-To circumvent this problem, another tagging method unchanged by cell death could be used.
+To circumvent this problem, another tagging method unaffected by cell death could be used.
 For example, a highly specific antibody to \textit{Pseudomonas putida} could be engineered.

### 2017-12-14 Data_csv/Paper/paper.tex
Evan's corrections

@@
 Our results are encouraging and would deserve some further experimentations.
-However, our results indicate that the Sand Community was almost entirely replaced by \textit{Pseudomonas veronii} or \textit{putida}.
+However, unlike usual bioaugmentation experiments in literature, our results indicate that the Sand Community was almost entirely replaced by \textit{Pseudomonas veronii} or \textit{putida}.
 
@@
 Every few hours (see Fig.
-\ref{design_weeks} for precise times), we took 2 samples from each flask to make technical replicates, and stained them with 4 µL SYTO-9 (50 µM), a  green fluorescent nucleic acid stain\footnote{ref.
+\ref{design_weeks} for precise times), we took 3 samples from each flask to make technical replicates, and stained them with 4 µL SYTO-9 (50 µM), a  green fluorescent nucleic acid stain\footnote{ref.
 https://www.thermofisher.com/order/catalog/product/S34854, Nov.
@@
 	\includegraphics[width=9cm]{AUCsc1.png}
-	\caption{Week 1 - SC : AUC (Area Under the Curve). Each point represents the mean of the 2 technical replicates.}
+	\caption{Week 1 - SC : AUC (Area Under the Curve). Each point represents the data from each well of the plate.}
 	\label{aucscw1}
@@
 	\includegraphics[width=9cm]{AUCpp1.png}
-	\caption{Week 2 - PP : AUC (Area Under the Curve). Each point represents the mean of the 2 technical replicates.}
+	\caption{Week 2 - PP : AUC (Area Under the Curve). Each point represents the data from each well of the plate.}
 	\label{aucppw1}
@@
 	\includegraphics[width=9cm]{AUCsc2.png}
-	\caption{Week 2 - SC : AUC (Area Under the Curve). Each point represents the mean of the 2 technical replicates.}
+	\caption{Week 2 - SC : AUC (Area Under the Curve). Each point represents the data from each well of the plate.}
 	\label{aucscw2}
@@
 	\includegraphics[width=9cm]{AUCpv2.png}
-	\caption{Week 2 - PV : AUC (Area Under the Curve). Each point represents the mean of the 2 technical replicates.}
-	\label{aucppw2}
+	\caption{Week 2 - PV : AUC (Area Under the Curve). Each point represents the data from each well of the plate.}
+	\label{aucpvw2}
 \end{figure}
@@
  Indeed, the fact that we get a green-only fluorescence in PP and PV alone is surprising, knowing that both PP and PV were tagged with mCherry, which emits a red fluorescence and causes an upwards shift in the fluorescence graph (as explained in Fig.
-\ref{scatterplot}).
+\ref{scatter1} and \ref{scatter2}).
 Moreover, the number of green-fluorescent cells in PP or PV alone looks a lot like the number in PPSC (Fig.
@@
 
-It is even more visible in Fig.\ref{problemflow}; Fig.\ref{problemflow1} is a representation of PP alone in toluene, and Fig.\ref{problemflow2}) of PPSC in toluene.
+It is even more visible in Fig.\ref{problemflow}.
+Fig.\ref{problemflow1} is a representation of PP alone in toluene, and Fig.\ref{problemflow2} of PPSC in toluene.
 These graphs are almost identical, and both show a green-only fluorescence.

### 2017-12-14 Data_csv/Paper/paper.tex
s

@@
 \begin{figure}
-
-	\begin{minipage}{.48\linewidth}
-	%	\hspace{-0.3cm}
-	%	\begin{subfigure}{.25\textwidth}
+		\hspace{-0.3cm}
+		\begin{subfigure}{.25\textwidth}
 			\centering			
-
-			\includegraphics[width=1\linewidth]{t8_unstained_ppsc1.png}
-			\captionof{figure}{Data of unstained sample (unstained PPSC, replicate 1, timepoint 8). Horizontal axis : intensity of red fluorescence. Vertical axis : intensity of green fluorescence.}
+			\includegraphics[width=4.3cm]{t8_unstained_ppsc1.png}
+			\caption{}
 			\label{scatter1}			
-
-	%	\end{subfigure}%
-	%	\begin{subfigure}{.22\textwidth}
-	\end{minipage}\hspace{.2cm}
-	\begin{minipage}{.48\linewidth}
-
+		\end{subfigure}%
+		\begin{subfigure}{.22\textwidth}		
 			\centering			
-
-			\includegraphics[width=1\linewidth]{t8_stained_ppsc1.png}
-			\captionof{figure}{Data of stained sample (stained PPSC, replicate 1, timepoint 8). Horizontal axis : intensity of red fluorescence. Vertical axis : intensity of green fluorescence.}
+			\includegraphics[width=4.3cm]{t8_stained_ppsc1.png}
+			\caption{}
 			\label{scatter2}			
-
-	%	\end{subfigure}
-	%	\caption{Fig.
+		\end{subfigure}
+		\caption*{Fig.
 \ref{scatter1}: Data of unstained sample (unstained PPSC, replicate 1, timepoint 8).
-Fig.
+\\ Fig.
 \ref{scatter2}: Data of stained sample (stained PPSC, replicate 1, timepoint 8).
@@
 Vertical axis : intensity of green fluorescence.}
-	%	\label{scatterplot}
-	\end{minipage}
-
+		\label{scatterplot}
+		\vspace{-0.5cm}
 \end{figure}
@@
 \subsubsection{Sand Community}
-The growth of the sand community in each treatment for the first week is represented in Fig. \ref{SCgrowth1}.
+The growth of the sand community in each treatment for the first week is represented in Fig. \ref{aucscw1} and \ref{SCgrowth1}.
 There is an important interaction between the explicative variables (F = 26.62, df = 1, $p = 8.64\cdot 10 ^{-4}$).
-In mixed carbon, SC grows similarly in presence or absence of PP (black and blue curve).
-In toluene however, the presence of PP allows for a 1000-fold difference on average (red and yellow curves).
+In mixed carbon, SC grows similarly in presence or absence of PP (black and blue points).
+In toluene however, the presence of PP allows for a 1000-fold difference on average (red and yellow points).
 We conclude that the presence of PP affects SC differently depending on the media.
 In toluene, it allows for a better growth but has no effect in the mix carbon media.
-In addition, the effect of the media on SC is important in absence of PP.
-SC alone grows less in toluene than in mixed carbon.\newline
+In addition, the effect of the media on SC is important in
+\begin{figure}[H]
+	\centering
+	\includegraphics[width=9cm]{AUCsc1.png}
+	\caption{Week 1 - SC : Each point represents one of the three replicates's AUC for each treatment.}
+	\label{aucscw1}
+\end{figure}%
+\vspace{-0.4cm}
+\begin{figure}[H]
+	\centering
+	\includegraphics[width=9cm]{AUCpp1.png}
+	\caption{Week 1 - PP : Each point represents one of the three replicates's AUC for each treatment.}
+	\label{aucppw1}
+\end{figure}
+absence of PP. SC alone grows less in toluene than in mixed carbon.\newline
 %There is an important difference between the media (F =907.30, df = 1, $p = 2.36 \cdot 10^{-6}$). It is clearly shown on the Fig. \ref{PPgrowth1} (red and yellow curves vs black and blue curves).
@@
 %We conclude that SC has no effect on the growth of PP and that PP grows better in toluene only than in mixed carbon. It is certainly due the greater amount of carbon in the toluene media.
-\begin{figure}[H]
-	\centering
-	\includegraphics[width=9cm]{AUCsc1.png}
-	\caption{Week 1 - SC : AUC (Area Under the Curve). Each point represents the data from each well of the plate.}
-	\label{aucscw1}
-\end{figure}
-
-\begin{figure}[H]
-	\centering
-	\includegraphics[width=9cm]{AUCpp1.png}
-	\caption{Week 2 - PP : AUC (Area Under the Curve). Each point represents the data from each well of the plate.}
-	\label{aucppw1}
-\end{figure}
 
 \subsubsection{Pseudomonas putida}
-There is an important difference between the media (F =907.30, df = 1, $p = 2.36 \cdot 10^{-6}$). It is clearly shown on the Fig. \ref{PPgrowth1} (red and yellow curves vs black and blue curves).
+There is an important difference between the media (F =907.30, df = 1, $p = 2.36 \cdot 10^{-6}$).
+It is clearly shown on the Fig.
+\ref{aucppw1} and \ref{PPgrowth1} (red and yellow curves/points vs black and blue curves/points)).
 In contrast, our data shows no significant difference due to the presence or absence of the sand community and no interaction.
@@
 \end{figure}
-
+\vspace{-0.4cm}
 \begin{figure}[H]
@@
 \subsubsection{Sand Community}
-The growth of the sand community in each treatment for the second week is represented in Fig. \ref{SCgrowth2}.
-In contrast with the first week, SC was able to grow in toluene.
+The growth of the sand community in each treatment for the second week is represented in Fig. \ref{aucscw2} and \ref{SCgrowth2}.
+In contrast with the first week, SC was able to grow in toluene (red curves/points).
 It is not surprising, as a community extracted from sand is typically composed of many kinds of bacteria.
@@
 \subsubsection{Pseudomonas veronii}
-The growth of the PV in each treatment is represented in Fig. \ref{PVgrowth2}.
+The growth of the PV in each treatment is represented in Fig. \ref{aucpvw2} and \ref{PVgrowth2}.
 As in the first week, there is an important difference of growth between the media (F = 784.71, df = 1, $p = 2.85 \cdot 10^{-9}$).
-PP grew about a hundred-fold greater in toluene (red and orange) than in mixed carbon (black and blue curves).
-One can also notice that PP grew slightly less in presence of SC, in both media (blue and yellow compared to black and red curves).
+PP grew about a hundred-fold greater in toluene (red and orange) than in mixed carbon (black and blue curves/points).
+One can also notice that PP grew slightly less in presence of SC, in both media (blue and yellow compared to black and red curves/points).
 The difference in area under the curve is significant (F = 5.56, df = 1, $p = 0.046$).While not being as significant as our other results, it seems to indicate some competition between them in this type of culture.
@@
 	\includegraphics[width=9cm]{AUCsc2.png}
-	\caption{Week 2 - SC : AUC (Area Under the Curve). Each point represents the data from each well of the plate.}
+	\caption{Week 2 - SC : Each point represents one of the three replicates's AUC for each treatment.}
 	\label{aucscw2}
-\end{figure}
-
+\end{figure}%
+\vspace{-0.3cm}
 \begin{figure}[H]
@@
 	\includegraphics[width=9cm]{AUCpv2.png}
-	\caption{Week 2 - PV : AUC (Area Under the Curve). Each point represents the data from each well of the plate.}
+	\caption{Week 2 - PV : Each point represents one of the three replicates's AUC for each treatment.}
 	\label{aucpvw2}
@@
 This led us to think that PP and PV would be interesting candidates for bioaugmentation, especially as they have no problem growing with SC in mixed carbon.
-In addition, it seems that PP has a good growth in presence of SC, while PV has low growth in presence of SC.
-It makes PP a better candidate than PV for bioaugmentation.
-Further experiments would be required to know if this is also true in a sand medium and especially over a longer period of time.
+
+As PV showed a significantly lower growth on average in toluene in presence of SC than PP, it would be tempting to say that PP would be an even better candidate.
+However, as said in results section B2, our data isn't totally reliable to compare the two strains, as the SC extracted the two weeks behaved differently.
+It would be good to test the PP and PV on the same SC.
+
+Further experiments would be required to know if this is also true in a sand medium (and not liquid medium) and especially over a longer period of time.
 Similar experiments could also be performed on different native communities.
@@
 \begin{figure}
-
 		\centering
@@
 
+%$\displaystyle\frac{\text{nbr of colonies } \cdot \text{ dilution factor } \cdot \text{ 100 $\mu$L of 1mL total}}{\text{estimated orginal number of cells}} = $\\
+%
+%
+%$\displaystyle\frac{1109 \cdot 25 \cdot 10}{2\cdot 10^{9}}= 1.39 \cdot 10 ^{-4}$
+
 \vspace*{\fill}

### 2017-12-15 Data_csv/Paper/paper.tex
vic. corrections

@@
 Our results are encouraging and would deserve some further experimentations.
-However, unlike usual bioaugmentation experiments in literature, our results indicate that the Sand Community was almost entirely replaced by \textit{Pseudomonas veronii} or \textit{putida}.
+However, unlike usual bioaugmentation experiments in literature, our results indicate that the Sand Community was almost entirely replaced by \textit{Pseudomonas veronii} or \textit{Pseudomonas putida}.
 
@@
 
-Our hypothesis for this experiment were that the addition of \textit{Pseudomonas putida} or \textit{Pseudomonas veronii} will have an effect on SC growth, especially in a toluene-only media, because we think that these strains might produce metabolites the SC could use as carbon source or reduce the toluene concentration and thus its toxic effect.
-This would lead to a better growth of the sand community in presence of one of these \textit{Pseudomonas} strains.
+Our hypothesis for this experiment were that the addition of PP or PV will have an effect on SC growth, especially in a toluene-only media, because we think that these strains might produce metabolites the SC could use as carbon source or reduce the toluene concentration and thus its toxic effect.
+This would lead to a better growth of SC in presence of one of either PP or PV.
 
@@
 
-We separated the work into two weeks, and tested a different \textit{Pseudomonas} strain each time. In each experiment, we tested 2 species and their interaction in mixed carbon and toluene.
+We separated the work into two weeks, testing SC and PP during Week 1 and SC and PV during Week 2. In each experiment, we tested the 2 communities and their interaction in mixed carbon and toluene.
 
@@
 Toluene being volatile, it will then evaporate and dissolve in the liquid media.
-It will then be the only source of carbon.
+It will be the only source of carbon.
 We quantified the cells using flow cytometry, and calculated to put $10^{6}$ cells/mL in PV/PP alone flasks, SC flasks, and added twice $10^{6}$ cells in PPSC and PVSC flasks.
@@
 		\caption*{Fig.
-\ref{scatter1}: Data of unstained sample (unstained PPSC, replicate 1, timepoint 8).
+\ref{scatter1}: Data of unstained sample (unstained PPSC in toluene, replicate 1, timepoint 8).
 \\ Fig.
-\ref{scatter2}: Data of stained sample (stained PPSC, replicate 1, timepoint 8).
+\ref{scatter2}: Data of stained sample (stained PPSC in toluene, replicate 1, timepoint 8).
 Horizontal axis : intensity of red fluorescence.
@@
 
+The Fig.
+\ref{scatter1} and \ref{scatter2} are scatterplots of unstained (Fig.
+\ref{scatter1}) and stained (Fig.
+\ref{scatter2}) samples.
+The vertical axis shows the intensity of green fluorescence, while the horizontal axis shows the intensity of red fluorescence.
+
 On Fig.
-\ref{scatter1} is a scatter plot of an unstained sample of PPSC.
-On the vertical axis is represented red fluorescence.
-The horizontal axis shows green fluorescence.
-A big black cluster and a red one above it can be observed.
+\ref{scatter1} a big black cluster and a red one above it can be observed.
 The black cluster is composed of SC cells and remaining particles.
 They show  low red and green fluorescence values.
-The PP cells express mCherry and therefore show red fluorescence, which causes an upwards shift on the plot, forming the red cluster above.
+The PP cells express mCherry and therefore show strong red fluorescence, which causes an upwards shift on the plot, forming the red cluster above.
 
@@
 \ref{scatter2} is a scatterplot of a sample from the same culture at the same timepoint but stained with SYTO-9.
-The SYTO-9 binds DNA and stains all the cells (\textit{Pseudomonas} and Sand Community alike) with a green fluorescence, which causes them to shift to the right side.
+The SYTO-9 binds DNA and stains all the cells (PP alike) with a green fluorescence, which causes them to shift to the right side.
 However, the red fluorescence value still allows for a distinction between PP/PV and SC.

### 2017-12-16 Data_csv/Paper/paper.tex
fiiinaaaal ??

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \begin{abstract}
-
-%	One of the crucial objectives after an environmental pollution is to recolonise the area.
-The first to do that are usually microorganisms, therefore helping them and understand this procedure is one of the important challenges of our time.
-Using bioaugmentation to help a community regrow is a recent method that can be used to fight against pollution.
-The two microorganism we chose for our experiment are \textit{Pseudomonas putida} and \textit{Pseudomonas veronii}, as they are able to degrade a widely used hydrocarbonate, toluene.
-We wanted to know if the addition of one of these strain to a bacterial community extracted from sand would have an effect on the growth of this community.
-In this experiment we worked with toluene and a sand community extracted from St-Sulpice.
-Our results are encouraging and would deserve some further experimentations.
-In the experiment conditions, the final amount of \textit{Pseudomonas} cells was way higher than the Sand Community cells, which means that the overall community was quite different from the starting Sand Community.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{INTRODUCTION}
+\section{Introduction}
 %alternative beginning
@@
 
-\section{MATERIAL AND METHOD}
+\section{Material and method}
 
@@
 
-\section{RESULTS}
+\section{Results}
 \subsection{Week 1 $\textendash$ SC, PP, PPSC}
@@
 
-\section{DISCUSSION}
+\section{Discussion}
 %While these results are promising, further analysis and plotting were carried out to ensure reliability of our results. 
@@
 For example growing the cells in sand would certainly affect their growth and fitness.
+%
 
-Firstly, in other bioaugmentation experiments, one of the main challenges is the survival of the inoculated strain in presence of a bacterial community \cite{bouchez} \cite{oldarticle}, particularly in absence of pollutant \cite{nodrawback}.
+%We noticed a slight drawback when we plotted the count of SYTO-9 stained cells over time, for PP alone and PPSC in toluene in Fig. \ref{problemw1} and \ref{problemw2}.
 
-In our experiments, PP and PV were able to grow in both media in presence or absence of SC.
-This led us to think that PP and PV would be interesting candidates for bioaugmentation, especially as they have no problem growing with SC in mixed carbon.
+\subsection{mCherry issue}
+The results are promising, however, there is a slight drawback.
+Some cells were detected in the SYTO-9 only gate in PP alone and PV alone cultures in both media (Fig.
+\ref{problemflow}).
+Fig.
+\ref{problemflow1} is a representation of PP alone in toluene, and Fig.
+\ref{problemflow2} of PPSC in toluene, both at the same timepoint.
+These graphs are almost identical, and more importantly, both show an important count in the SYTO-9 only gate (Fig.
+\ref{problemw1}, Fig.
+\ref{problemw2}).
+We also observe this phenomenon with PV alone.
+This is quite surprising, knowing that both PP and PV were tagged with mCherry. This protein emits a
+red fluorescence and should cause an upwards shift in the fluorescence graph (as explained in Fig. \ref{scatter1} and \ref{scatter2}) and bring these cells in the mChe + SYTO-9 gate.
 
-As PV showed a significantly lower growth on average in toluene in presence of SC than PP, it would be tempting to say that PP would be an even better candidate.
-However, as said in results section B2, our data isn't totally reliable to compare the two strains, as the SC extracted the two weeks behaved differently.
-It would be good to test the PP and PV on the same SC.
+Our hypothesis is that some PP/PV cells died, but weren’t lysed.
+Their DNA is still nicely protected  in the cell and can be stained by SYTO-9.
+However, their metabolic activities stopped, reducing mCherry fluorescence.
+Without the red tag, these cells would shift downwards and remain in the SYTO-9 only gate.
+It renders differentiation between PP (or PV) and SC seemingly impossible because they both appear in the same gate.
+A multivariate analysis using PCA (Principal Component Analysis) and K-means clustering was performed to try to differentiate the two controls (PP alone, SC alone) with other factors (forward-scatter and side-scatter for example), but to no avail.
 
-Further experiments would be required to know if this is also true in a sand medium (and not liquid medium) and especially over a longer period of time.
-Similar experiments could also be performed on different native communities.
-Also, it would be interesting to vary the concentration of toluene in these experiments.
+This issue makes us question whether the significant increase in AUC in the SYTO-9 only in PPSC compared to SC alone is due to an increase of the number of SC or to the presence of theses PP cells presenting low red fluorescence values.
 
-We noticed a slight drawback when we plotted the count of SYTO-9 stained cells over time, for PP alone and PPSC in toluene in Fig. \ref{problemw1} and \ref{problemw2}.
+To circumvent this problem, another tagging method unaffected by cell death could be used (Fig.
+\ref{antibody}).
+For example, a highly specific antibody to \textit{Pseudomonas putida} could be engineered.
+A secondary antibody, this time linked to a fluorescent protein would bind the first one and therefore mark all \textit{Pseudomonas putida} cells.
+This would allow a better differentiation of our communities.
 
@@
 		\includegraphics[width=9cm]{problemw1.PNG}
-		\caption{Total count of green stained cells in toluene for PP alone and PP with SC during week 1. It showed no significant differences.}
+		\caption{Total count of green stained cells in toluene for PP alone and PP with SC during week 1.
+It showed no significant differences.
+Each point is a replicate, and each line is the mean of the corresponding replicates.}
 		\label{problemw1}
@@
 		\includegraphics[width=9cm]{problemw2.PNG}
-		\caption{Total count of green stained cells in toluene for PV alone and PV with SC during week 2. It showed no significant differences.}
+		\caption{Total count of green stained cells in toluene for PV alone and PV with SC during week 2.
+It showed no significant differences.
+Each point is a replicate, and each line is the mean of the corresponding replicates.}
 		\label{problemw2}
@@
 
- Indeed, the fact that we get a green-only fluorescence in PP and PV alone is surprising, knowing that both PP and PV were tagged with mCherry, which emits a red fluorescence and causes an upwards shift in the fluorescence graph (as explained in Fig.
-\ref{scatter1} and \ref{scatter2}).
-Moreover, the number of green-fluorescent cells in PP or PV alone looks a lot like the number in PPSC (Fig.
-\ref{problemw1}) or PVSC (Fig.
-\ref{problemw2}).
-
-It is even more visible in Fig.\ref{problemflow}.
-Fig.\ref{problemflow1} is a representation of PP alone in toluene, and Fig.\ref{problemflow2} of PPSC in toluene.
-These graphs are almost identical, and both show a green-only fluorescence.
-
-Our hypothesis is that some PP/PV cells died, but weren’t lysed.
-Their DNA being still nicely protected they could be stained by SYTO-9.
-However, their metabolic activities stopped, reducing mCherry fluorescence.
-Without the red tag, these cells would shift downwards and remain in the SYTO-9 only gate and can't be differentiated from the SC cells.
 \begin{figure}
@@
 
-\subsection{Improvements}
+% Indeed, the fact that we get a green-only fluorescence in PP and PV alone is surprising, knowing that both PP and PV were tagged with mCherry, which emits a red fluorescence and causes an upwards shift in the fluorescence graph (as explained in Fig.
+\ref{scatter1} and \ref{scatter2}).
+Moreover, the number of green-fluorescent cells in PP or PV alone looks a lot like the number in PPSC (Fig.
+\ref{problemw1}) or PVSC (Fig.
+\ref{problemw2}).
+% 
+%It is even more visible in Fig.\ref{problemflow}.
+Fig.\ref{problemflow1} is a representation of PP alone in toluene, and Fig.\ref{problemflow2} of PPSC in toluene.
+These graphs are almost identical, and both show a green-only fluorescence.
+% 
+%
+%Our hypothesis is that some PP/PV cells died, but weren’t lysed.
+Their DNA being still nicely protected they could be stained by SYTO-9.
+However, their metabolic activities stopped, reducing mCherry fluorescence.
+Without the red tag, these cells would shift downwards and remain in the SYTO-9 only gate and can't be differentiated from the SC cells.
 
-To circumvent this problem, another tagging method unaffected by cell death could be used.
-For example, a highly specific antibody to \textit{Pseudomonas putida} could be engineered.
-A secondary antibody, this time linked to a fluorescent protein would bind the first one and therefore mark all \textit{Pseudomonas putida} cells.
-This would allow a better differentiation of our communities.
+%\subsection{Improvements}
+
+%Another point that could be interesting to change is the initial concentration of PP and PV.
+Indeed we used $10^{6}$ cells of SC and $10^{6}$ cells of PP or PV.
+Maybe by reducing the initial concentration of PP/PV, we could reduce their competition with SC over resources, and therefore observe a better growth for SC in toluene media.
+%
+%In addition, we inoculated the media with the same number of PP or PV with SC and haven't considered the fact that SC community is composed of different bacterial species.
+%The high quantity of a single strain may have made it easier for them  to outgrow SC over time.
+
+%Finally, as often in the lab, our results seem to unveil more questions than answers.
+We would have liked, if time allowed it, to perform additional experiments proposed above.
+Because in the present state, we got interesting results, but due to some unforeseeable events, we cannot be certain that they are not artefacts due to the issue differentiating the cells we mentioned before.
+%
+%Finally, the results of our study open new questions for which we need to perform additional experiments, such as those described above.
+The issue with this staining technique might carry some artefacts that should be considered in data interpretation.
 \begin{figure}[H]
@@
 \end{figure}
-Another point that could be interesting to change is the initial concentration of PP and PV.
-Indeed we used $10^{6}$ cells of SC and $10^{6}$ cells of PP or PV.
+\subsection{Bacterial interactions}
+To summarise, growing PP or PV with SC shows no effect on the total cell count compared to growing PP / PV alone. 
+\begin{figure}[H]
+	\centering
+
+	\includegraphics[width=8.5cm]{antibodytag.jpg}
+	\caption{Fluorescent antibody tagging, as an alternative to mCherry in this experiment}
+	\label{antibody}
+
+\end{figure}
+If we assume this tagging issue is negligible, we can infer on the growth of each population separately within each treatment.
+In the first week, the data indicates that the presence of PP affects SC differently depending on the media (Interaction: F = 26.62, df = 1, $p = 8,64 \cdot 10^{-4}$).
+In toluene, it allows a better growth but has no effect in the mix carbon media.
+There is an important effect of the media in absence of PP: SC alone grows significantly less in toluene than in mixed carbon.
+Furthermore, PP shows an important difference in AUC between the media (F =907.30, df = 1, $p = 2.36 \cdot 10^{-6}$) and no difference due to the presence of SC.
+
+During the second week, SC behaved differently: it was able to grow in the toluene media, even alone. No significant effect of the media nor of the addition of PV were highlighted by the Anova. 
+Similarly to PP, PV had a better growth in toluene than in mixed carbon (F = 784.71, df = 1,
+$p = 2.85 \cdot 10^{-9}$).
+This time however, there was a significant reduction of the number of PV in presence of SC in toluene (F =5.56, df = 1, $p = 0,046$).
+While not being as significant as our other results, it seems to indicate some competition between them in this type of culture.
+
+It might also be important to notice that even if the AUC of the SYTO-9 gate in PPSC is significantly higher than in SC alone, the proportion of SC in PPSC is very low (about 5%).
+
+To study more deeply these interaction, it might be interesting to change is the initial concentration of PP and PV.
+Indeed we used 10\textsuperscript{6} cells of SC and 10\textsuperscript{6} cells of PP or PV.
 Maybe by reducing the initial concentration of PP/PV, we could reduce their competition with SC over resources, and therefore observe a better growth for SC in toluene media.
 
-In addition, we inoculated the media with the same number of PP or PV with SC and haven't considered the fact that SC community is composed of different bacterial species.
+In addition, we inoculated the media with the same number of PP or PV with SC and haven’t considered the fact that SC community is composed of different bacterial species.
 The high quantity of a single strain may have made it easier for them to outgrow SC over time.
 
-%Finally, as often in the lab, our results seem to unveil more questions than answers.
-We would have liked, if time allowed it, to perform additional experiments proposed above.
-Because in the present state, we got interesting results, but due to some unforeseeable events, we cannot be certain that they are not artefacts due to the issue differentiating the cells we mentioned before.
-%
-%Finally, the results of our study open new questions for which we need to perform additional experiments, such as those described above.
-The issue with this staining technique might carry some artefacts that should be considered in data interpretation.
+\subsection{Back to context}
+In many bioaugmentation experiments, one of the main challenges is the survival of the inoculated strain in presence of a bacterial community \cite{bouchez} \cite{oldarticle}, particularly in absence of pollutant \cite{nodrawback}.
 
-In conclusion, in the present state, our study shows interesting results.
+In our experiments, PP and PV were able to grow in both media in presence or absence of SC.
+This led us to think that PP and PV would be interesting candidates for bioaugmentation, especially as they have no problem growing with SC in mixed carbon.
+
+As PV showed a significantly lower growth on average in toluene in presence of SC than PP, it would be tempting to say that PP would be an even better candidate.
+However, as said in \textit{Results} section \textit{B2}, our data isn't totally reliable to compare the two strains, as the SC extracted the two weeks behaved differently.
+It would be good to test the PP and PV on the same SC.
+
+Further experiments would be required to know if this is also true in a sand medium (and not liquid medium) and especially over a longer period of time.
+Similar experiments could also be performed on different native communities.
+Also, it would be interesting to vary the concentration of toluene in these experiments.
+
+\subsection{Conclusion}
+
+In the present state, our study shows interesting results.
 However, the issue with this staining technique might carry some artefacts that should be considered in data interpretation.
@@
 \clearpage
-APPENDIX A
+\section*{Appendix A}
 
@@
 	\begin{figure}
-		APPENDIX B
+		\section*{Appendix B}
 

### 2017-12-17 Data_csv/Paper/paper.tex
typos

@@
 It is likely that at least one of them can degrade a given carbon source.
-But it shows that the sand community we extracted behaved differently from one week to another and thus cannot be considered similar.
+But it shows that SC behaved differently from one week to another and thus cannot be considered identical.
 Therefore, we won't be able to compare the results from the two weeks.
-The anova on the area under the curve shows no significant effect of any explicative variables, but we believe the results could be different if we continued the culture for a day because we can see on the growth graph that SC alone is still in exponential growth at 48 hours in toluene.
+The Anova on the area under the curve shows no significant effect of any explicative variables, but we believe the results could be different if we continued the culture for a day because we can see on the growth graph that SC alone is still in exponential growth at 48 hours in toluene.
 It is plausible that with a few more timepoints, SC would grow better alone than in presence of PV.\newline
@@
 \subsubsection{Pseudomonas veronii}
-The growth of the PV in each treatment is represented in Fig. \ref{aucpvw2} and \ref{PVgrowth2}.
+The growth of PV in each treatment is represented in Fig. \ref{aucpvw2} and \ref{PVgrowth2}.
 As in the first week, there is an important difference of growth between the media (F = 784.71, df = 1, $p = 2.85 \cdot 10^{-9}$).
-PP grew about a hundred-fold greater in toluene (red and orange) than in mixed carbon (black and blue curves/points).
+PP grew about a hundred-fold better in toluene (red and orange) than in mixed carbon (black and blue curves/points).
 One can also notice that PP grew slightly less in presence of SC, in both media (blue and yellow compared to black and red curves/points).
-The difference in area under the curve is significant (F = 5.56, df = 1, $p = 0.046$).While not being as significant as our other results, it seems to indicate some competition between them in this type of culture.
+The difference in area under the curve is significant (F = 5.56, df = 1, $p = 0.046$).While not being as significant as our other results, it could be an indication some competition between them in this type of culture.
 It seems plausible, knowing from previous experiments that PV grows a bit slower than PP and in this experiment some bacteria from the sand community were able to grow on toluene.
@@
 \subsection{mCherry issue}
-The results are promising, however, there is a slight drawback.
+Further analysis was carried out to ensure the reliability of our promising results. It brought a slight drawback to light.
 Some cells were detected in the SYTO-9 only gate in PP alone and PV alone cultures in both media (Fig.
@@
 However, their metabolic activities stopped, reducing mCherry fluorescence.
-Without the red tag, these cells would shift downwards and remain in the SYTO-9 only gate.
+Without the red tag, these cells would shift downwards and into the SYTO-9 only gate.
 It renders differentiation between PP (or PV) and SC seemingly impossible because they both appear in the same gate.
@@
 
-This issue makes us question whether the significant increase in AUC in the SYTO-9 only in PPSC compared to SC alone is due to an increase of the number of SC or to the presence of theses PP cells presenting low red fluorescence values.
+This issue makes us question whether the significant increase in AUC in the SYTO-9 only in PPSC compared to SC alone is due to an increase of the number of SC or to the presence of PP cells presenting low red fluorescence values.
 
@@
 The issue with this staining technique might carry some artefacts that should be considered in data interpretation.
-\begin{figure}[H]
-	\centering
 
-	\includegraphics[width=8.5cm]{antibodytag.jpg}
-	\caption{Fluorescent antibody tagging, as an alternative to mCherry in this experiment}
-	\label{antibody}
-
-\end{figure}
 \subsection{Bacterial interactions}
@@
 
-It might also be important to notice that even if the AUC of the SYTO-9 gate in PPSC is significantly higher than in SC alone, the proportion of SC in PPSC is very low (about 5%).
+It might also be important to notice that even if the AUC of the SYTO-9 gate in PPSC is significantly higher than in SC alone, the proportion of SC in PPSC is very low (about 5\%).
 
-To study more deeply these interaction, it might be interesting to change is the initial concentration of PP and PV.
+To study more deeply these interaction, it might be interesting to change the initial concentration of PP and PV.
 Indeed we used 10\textsuperscript{6} cells of SC and 10\textsuperscript{6} cells of PP or PV.
@@
 In addition, we inoculated the media with the same number of PP or PV with SC and haven’t considered the fact that SC community is composed of different bacterial species.
-The high quantity of a single strain may have made it easier for them to outgrow SC over time.
+The high quantity of a single strain (PP or PV) may have made it easier for them to outgrow SC over time.
 
@@
 However, as said in \textit{Results} section \textit{B2}, our data isn't totally reliable to compare the two strains, as the SC extracted the two weeks behaved differently.
-It would be good to test the PP and PV on the same SC.
+It would be good to test PP and PV on the same SC.
 

### 2017-12-19 Data_csv/Paper/paper.tex
ss

@@
 Every surface, soil or liquid in our environment is colonized by multiple microorganisms, interacting with each other and forming communities.
-However, the whole complexity of the interactions is still today not always fully understood.
-In addition, these communities also interact with other organisms and can be perturbed by the effects of pollution such as spillage of oil or solvent.
+However, the whole complexity of the interactions still isn't fully understood today.
+In addition, these communities also interact with other organisms and can be perturbed by the effects of pollution such as oil or solvent spillage.
 We decided to use toluene as a pollutant for this experiment.
 
-Toluene is an organic solvent widely used in industry nowadays, as a paint solvent or as extraction solvent in the cosmetic industry.
-Toluene is a monoaromatic volatile molecule which is toxic and ecotoxic \cite{toluene}.
+Toluene is an organic solvent widely used in the paint or cosmetic industry nowadays. It is a monoaromatic volatile molecule which is toxic and ecotoxic \cite{toluene}. 
 When such event happens, one way to treat it is the use of bioremediation.
@@
 Our hypothesis for this experiment were that the addition of PP or PV will have an effect on SC growth, especially in a toluene-only media, because we think that these strains might produce metabolites the SC could use as carbon source or reduce the toluene concentration and thus its toxic effect.
-This would lead to a better growth of SC in presence of one of either PP or PV.
+This would lead to a better growth of SC in presence of either PP or PV.
 
-\section{Material and method}
+\section{Materials and methods}
 
@@
 One can also notice that PP grew slightly less in presence of SC, in both media (blue and yellow compared to black and red curves/points).
-The difference in area under the curve is significant (F = 5.56, df = 1, $p = 0.046$).While not being as significant as our other results, it could be an indication some competition between them in this type of culture.
+The difference in area under the curve is significant (F = 5.56, df = 1, $p = 0.046$).
+While not being as significant as our other results, it could indicate some competition between them in this type of culture.
 It seems plausible, knowing from previous experiments that PV grows a bit slower than PP and in this experiment some bacteria from the sand community were able to grow on toluene.

### 2017-12-22 Data_csv/Paper/paper.tex
last and final and that's all

@@
 \begin{abstract}
+In case of an environmental pollution, the microbial community of the soil will have an important role in the degradation of the pollutant.
+However, adaptation to the sudden change in the soil composition is difficult for most bacterial communities.
+But bioaugmentation, the addition of a bacteria able to degrade a pollutant in order to remove that pollutant from the environment, might also have positive side effects on the growth of the original bacterial community.
+Furthermore, the survival of the added bacteria and thus the efficiency of bioaugmentation depends a lot on its capacity to grow in presence of the original bacterial community.
+In that context, we chose to study the interaction of a bacterial community extracted from sand and two toluene degrading bacteria: \textit{Pseudomonas putida} F1  or \textit{Pseudomonas veronii} YdBTEX2 (both tagged with fluorescent mCherry protein).
+To do so, we grew them in batch cultures either with toluene only or with mixed carbon\footnote{Mixed Carbon media composition : L-Arginine, D-Xylose, Aspartic acid potassium salt, 2-Hydroxybenzoic acid, L-Phenylalanine, L-Serine, Gamma Hydroxy butyric acid, D-cellobiose, alpha-D-Lactose, Putrescine, Itaconic acid, alpha-D-Glucose-1-phosphate, D-Glucosaminic acid, N-acetyl-D-glucosamine, 4-Hydroxy benzoic acid, D-Mannitol, meso-erytritol, Galacturonic acid, Methyl pyruvate, Tween 20.
+Each component in equal concentration} substrate.
+We used flow cytometry at different time points to measure the growth of each population separatly.
+If we consider negligible the difficulty we had to distingish the two populations (see \textit{Discussion}), our results notably indicate that the bacterial commnuity grows better in toluene in presence of \textit{Pseudomonas putida} F1 than alone.
 
-In the case of an environmental pollution, the microbial community of the soil will have an important role in the degradation of the pollutant.
+%In the case of an environmental pollution, the microbial community of the soil will have an important role in the degradation of the pollutant.
 However, adaptation to the sudden change in the soil composition is difficult for most bacterial communities.
@@
 It is the addition of bacteria able to degrade the pollutant into the contaminated environment.
-In our experiment, we chose to add \textit{Pseudomonas veronii} 1YdBTEX2 and \textit{Pseudomonas putida F1} (both tagged with fluorescent mCherry protein) to a bacterial community extracted from sand and to grow them either with toluene only or with mixed carbon\footnote{Mixed Carbon media composition : L-Arginine, D-Xylose, Aspartic acid potassium salt, 2-Hydroxybenzoic acid, L-Phenylalanine, L-Serine, Gamma Hydroxy butyric acid, D-cellobiose, alpha-D-Lactose, Putrescine, Itaconic acid, alpha-D-Glucose-1-phosphate, D-Glucosaminic acid, N-acetyl-D-glucosamine, 4-Hydroxy benzoic acid, D-Mannitol, meso-erytritol, Galacturonic acid, Methyl pyruvate, Tween 20.
-Each component in equal concentration} substrate.
+In our experiment, we chose to add \textit{Pseudomonas veronii} 1YdBTEX2 and \textit{Pseudomonas putida F1} (both tagged with fluorescent mCherry protein) to a bacterial community extracted from sand and to grow them either with toluene only or with mixed carbon substrate.
 As the two \textit{Pseudomonas} strains we added are able to degrade toluene, we wanted to know if the addition of one of these strain to this bacterial community would have an effect on the growth of this community.
-Our results are encouraging and would deserve some further experimentations.
+%Our results are encouraging and would deserve some further experimentations.
 However, unlike usual bioaugmentation experiments in literature, our results indicate that the Sand Community was almost entirely replaced by \textit{Pseudomonas veronii} or \textit{Pseudomonas putida}.
@@
 There are several different techniques of bioremediation but they all have the same purpose: to use live organisms to get rid of pollutants.
-The technique that interested us in this experiment was bioaugmentation, the addition of a microorganism able to degrade the targeted pollutant to a native community, allowing it to grow back \cite{Bioremediation}.
+The technique that interested us in this experiment was bioaugmentation, the addition of a microorganism able to degrade the targeted pollutant in order to remove that pollutant from the environment \cite{Bioremediation}.
+We wanted to know if that also had a potentially positive side effects on the original bacterial community's growth.
 
@@
 
-%ALTERNATIVE 1
-
-%In our experiment we wanted to know if this ability to metabolize toluene could not only have a positive effect on a native community, for example by lowering the toluene concentration or by producing metabolites that the bacteria from SC could use as carbon source.
-Our hypothesis for this experiment was that the addition of \textit{Pseudomonas putida} or \textit{Pseudomonas veronii} will have an effect on SC growth, especially in a toluene-only media.
-%ALTERNATIVE 2
-
-%Our hypothesis for this experiment was that the addition of Pseudomonas putida or Pseudomonas veronii will have an effect on SC growth, especially in a toluene-only media.
-%Ideed, we think that these Pseudomonas bacteria could produce metabolites the SC bacteria could use as carbon source or reduce the toluene concentration and thus it's toxic effect.
-This would lead to a better growth of the sand community in presence of one of these pseudomonas strains.
-
 Our hypothesis for this experiment were that the addition of PP or PV will have an effect on SC growth, especially in a toluene-only media, because we think that these strains might produce metabolites the SC could use as carbon source or reduce the toluene concentration and thus its toxic effect.
@@
 \subsection{Experimental design}
-Apart from SC, we used two bacterial strains : \textit{Pseudomonas veronii} 1YdBTEX2 (tagged with mCherry) and \textit{Pseudomonas putida F1}(also tagged with mCherry).
-
-However, keep in mind that SC isn't a single species of bacteria, but rather a community containing potentially many different species.
-%There were 3 bacterial cultures used for this experiment: \textit{Pseudomonas veronii} 1YdBTEX2 (tagged with mCherry, called PV), \textit{Pseudomonas putida F1}(tagged with mCherry, called PP) and a Sand Community, extracted from the beach of St-Sulpice.
+Apart from SC, we used two bacterial strains : \textit{Pseudomonas veronii} 1YdBTEX2 (tagged with mCherry) and \textit{Pseudomonas putida F1}(also tagged with mCherry).However, keep in mind that SC isn't a single species of bacteria, but rather a community containing potentially many different species.
 We experimented with two media: a mixed carbon medium\textsuperscript{1} and a Minimal Media 1x (MM) with only toluene as carbon source.
-
-We separated the work into two weeks, testing SC and PP during Week 1 and SC and PV during Week 2. In each experiment, we tested the 2 communities and their interaction in mixed carbon and toluene.
-
+We separated the work into two weeks, testing SC and PP during Week 1 and SC and PV during Week 2.
+In each experiment, we tested the 2 communities and their interaction in mixed carbon and toluene (see Fig.
+\ref{design_weeks}).
+As controls, we used SC alone in both media, to prove that the medium has an effect and compare with the interaction of species.
+PP(or PV) alone in both media are used to show that the medium has no effect.
 \begin{figure}[H]
-
 	\includegraphics[width=9cm]{erlenmeyer.PNG}
@@
 \end{figure}
-
-As controls, we used SC alone in both media, to prove that the medium has an effect and compare with the interaction of species.
-PP(or PV) alone in both media are used to show that the medium has no effect.
 We therefore had 6 unique treatments, and used 3 replicates for each.
@@
 In toluene however, the presence of PP allows for a 1000-fold difference on average (red and yellow points).
-We conclude that the presence of PP affects SC differently depending on the media.
-In toluene, it allows for a better growth but has no effect in the mix carbon media.
-In addition, the effect of the media on SC is important in
+
+We conclude that the presence of PP affects SC differently depending on the media. In toluene, it allows for a  better growth but has no effect in the mix carbon media. 
 \begin{figure}[H]
@@
 	\label{aucppw1}
-\end{figure}
-absence of PP. SC alone grows less in toluene than in mixed carbon.\newline
+\end{figure}In addition, the effect of the media on SC is important in absence of PP. SC alone grows less in toluene than in mixed carbon.\newline
 %There is an important difference between the media (F =907.30, df = 1, $p = 2.36 \cdot 10^{-6}$). It is clearly shown on the Fig. \ref{PPgrowth1} (red and yellow curves vs black and blue curves).
@@
 \ref{totcountmixC2text} and \ref{totcounttol2text}, the conclusion is the same as in the first week.
-It shows no signs that growing PV and SC together influences the growth of the overall population nor the total cell count after 48 hours, in a mixed carbon or toluene media.\newline
+It shows no signs that growing PV and SC together influences the growth of the overall population nor the total cell count after 48 hours, in a mixed carbon or toluene media.
 
-\begin{figure}[H]
+\begin{figure}
 	\centering
@@
 \end{figure}
-\vspace{-0.4cm}
-\begin{figure}[H]
-	\centering
-	\includegraphics[width=9cm]{totcount_tol2.PNG}
-	\caption{Total count (SYTO-9 count + mCherry count) of SC, PV and PVSC over time in a toluene only medium during the second week.}
-	\label{totcounttol2text}
-\end{figure}
+
 \subsubsection{Sand Community}
@@
 Therefore, we won't be able to compare the results from the two weeks.
+
 The Anova on the area under the curve shows no significant effect of any explicative variables, but we believe the results could be different if we continued the culture for a day because we can see on the growth graph that SC alone is still in exponential growth at 48 hours in toluene.
-It is plausible that with a few more timepoints, SC would grow better alone than in presence of PV.\newline
+It is plausible that with a few more timepoints, SC would grow better alone than in presence of PV.
 
@@
 PP grew about a hundred-fold better in toluene (red and orange) than in mixed carbon (black and blue curves/points).
-One can also notice that PP grew slightly less in presence of SC, in both media (blue and yellow compared to black and red curves/points).
-The difference in area under the curve is significant (F = 5.56, df = 1, $p = 0.046$).
-While not being as significant as our other results, it could indicate some competition between them in this type of culture.
-It seems plausible, knowing from previous experiments that PV grows a bit slower than PP and in this experiment some bacteria from the sand community were able to grow on toluene.
-\newline
 
+One can also notice that PP grew slightly less in presence of SC, \begin{figure}[H]
+	\centering
+	\includegraphics[width=9cm]{totcount_tol2.PNG}
+	\caption{Total count (SYTO-9 count + mCherry count) of SC, PV and PVSC over time in a toluene only medium during the second week.}
+	\label{totcounttol2text}
+\end{figure}
+\vspace{-0.5cm}
 \begin{figure}[H]
@@
 \end{figure}%
-\vspace{-0.3cm}
+\vspace{-0.4cm}
 \begin{figure}[H]
@@
 	\label{aucpvw2}
-\end{figure}
+\end{figure}in both media (blue and yellow compared to black and red curves/points). 
+The difference in area under the curve is significant (F = 5.56, df = 1, $p = 0.046$). 
+While not being as significant as our other results, it could indicate some competition between them in this type of culture.
+It seems plausible, knowing from previous experiments that PV grows a bit slower than PP and in this experiment some bacteria from the sand community were able to grow on toluene.
+\newline
 
@@
 This would allow a better differentiation of our communities.
+\begin{figure}[H]
+	\centering
 
-\begin{figure}
+	\includegraphics[width=8.5cm]{antibodytag.jpg}
+	\caption{Fluorescent antibody tagging, as an alternative to mCherry in this experiment}
+	\label{antibody}
+
+\end{figure}
+
+\subsection{Bacterial interactions}
+To summarise, growing PP or PV with SC shows no effect on the total cell count compared to growing PP / PV alone. 
+\begin{figure}[H]
 	\centering
@@
 
-\begin{figure}
+\begin{figure}[H]
 	\centering
@@
 	\label{problemw2}
-
-%\caption{Fig.
-\ref{problemw1} : Total count of green stained cells in toluene for PP alone and PP with SC during week 1.
-It showed no significant differences.
-Fig.
-\ref{problemw2} : Total count of green stained cells in toluene for PV alone and PV with SC during week 2.
-It showed no significant differences.}
-%\label{problemsyto}
-
 \end{figure}
 
-\begin{figure}
+\begin{figure}[H]
 	\hspace{-0.3cm}
@@
 	\label{problemflow}
-\end{figure}
-
-% Indeed, the fact that we get a green-only fluorescence in PP and PV alone is surprising, knowing that both PP and PV were tagged with mCherry, which emits a red fluorescence and causes an upwards shift in the fluorescence graph (as explained in Fig.
-\ref{scatter1} and \ref{scatter2}).
-Moreover, the number of green-fluorescent cells in PP or PV alone looks a lot like the number in PPSC (Fig.
-\ref{problemw1}) or PVSC (Fig.
-\ref{problemw2}).
-% 
-%It is even more visible in Fig.\ref{problemflow}.
-Fig.\ref{problemflow1} is a representation of PP alone in toluene, and Fig.\ref{problemflow2} of PPSC in toluene.
-These graphs are almost identical, and both show a green-only fluorescence.
-% 
-%
-%Our hypothesis is that some PP/PV cells died, but weren’t lysed.
-Their DNA being still nicely protected they could be stained by SYTO-9.
-However, their metabolic activities stopped, reducing mCherry fluorescence.
-Without the red tag, these cells would shift downwards and remain in the SYTO-9 only gate and can't be differentiated from the SC cells.
-
-%\subsection{Improvements}
-
-%Another point that could be interesting to change is the initial concentration of PP and PV.
-Indeed we used $10^{6}$ cells of SC and $10^{6}$ cells of PP or PV.
-Maybe by reducing the initial concentration of PP/PV, we could reduce their competition with SC over resources, and therefore observe a better growth for SC in toluene media.
-%
-%In addition, we inoculated the media with the same number of PP or PV with SC and haven't considered the fact that SC community is composed of different bacterial species.
-%The high quantity of a single strain may have made it easier for them  to outgrow SC over time.
-
-%Finally, as often in the lab, our results seem to unveil more questions than answers.
-We would have liked, if time allowed it, to perform additional experiments proposed above.
-Because in the present state, we got interesting results, but due to some unforeseeable events, we cannot be certain that they are not artefacts due to the issue differentiating the cells we mentioned before.
-%
-%Finally, the results of our study open new questions for which we need to perform additional experiments, such as those described above.
-The issue with this staining technique might carry some artefacts that should be considered in data interpretation.
-
-\subsection{Bacterial interactions}
-To summarise, growing PP or PV with SC shows no effect on the total cell count compared to growing PP / PV alone. 
-\begin{figure}[H]
-	\centering
-
-	\includegraphics[width=8.5cm]{antibodytag.jpg}
-	\caption{Fluorescent antibody tagging, as an alternative to mCherry in this experiment}
-	\label{antibody}
-
 \end{figure} 
